---
name: Antonio
surname: Páez
position: "Professor"
address: |
         | School of Earth, Environment and Society
         | McMaster University
         | 1280 Main St West, Hamilton, Ontario, Canada L8S 1S4
         | phone: +1 905 525 9140
www: experts.mcmaster.ca/display/paezha
email: "paezha@mcmaster.ca"
orcid: 0000-0001-6912-9919
github: paezha
publons: 2897251
#researchgate: 7004827878
googlescholar: paezha
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    page_total: true
    extra_dependencies: ["flafter"]
header-includes:
  - \usepackage{soul}
  - \usepackage{longtable}
  - \usepackage{float}
---


```{r knitr-setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE,
                      fig.show='asis', 
                      out.width="0.6\\linewidth", 
                      fig.align='center')

#pandoc::pandoc_activate()
```

```{r load-packages}
library(bibliometrix) # Comprehensive Science Mapping Analysis
library(dplyr) # A Grammar of Data Manipulation
library(ggraph) # An Implementation of Grammar of Graphics for Graphs and Networks
library(ggplot2) # Create Elegant Data Visualisations Using the Grammar of Graphics
library(glue) # Interpreted String Literals # Interpreted String Literals
library(gt) # Easily Create Presentation-Ready Display Tables
library(here) # A Simpler Way to Find Your Files # A Simpler Way to Find Your Files
library(kableExtra) # Construct Complex Table with 'kable' and Pipe Syntax 
library(lubridate) # Make Dealing with Dates a Little Easier
library(maps) # Draw Geographical Maps
library(readr) # Read Rectangular Text Data
library(rnaturalearth) # World Map Data from Natural Earth
library(rnaturalearthdata) # World Vector Map Data from Natural Earth Used in 'rnaturalearth'
library(scholar) # Analyse Citation Data from Google Scholar
library(sf) # Simple Features for R
library(stringr) # Simple, Consistent Wrappers for Common String Operations
library(tibble) # Simple Data Frames
library(tidygraph) # A Tidy API for Graph Manipulation
library(tidyr) # Tidy Messy Data
library(treemapify) # Draw Treemaps in 'ggplot2'
library(vitae) # Curriculum Vitae for R Markdown
```

```{r current-year}
# Retrieve current year
current_year <- lubridate::year(Sys.time()) # Update year
```

```{r google-scholar-id}
id <- "bLY377kAAAAJ" # Replace with your own google scholar id
```

```{r google-scholar-bibliometrics}
citations_scholar <- scholar::get_citation_history(id)
h_index <- get_profile(id)$h_index
i10_index <- get_profile(id)$i10_index
```

# About this CV

This CV was created programmatically using the `R` statistical language, and it can be accessed in folder `00-Official-CV` of this repository:

https://github.com/paezha/Official-CV/

# About Me

* I trained in civil engineering before being adopted into geography.
* My areas of interest include transportation, equity, justice, spatial analysis, spatial statistics, travel behavior, and cities.
* Also, too, mathematics, computer languages, science fiction, poetry, and history.
* My research has been funded by all three agencies in the Tri-Council: CIHR, NSERC, and SSHRC.
* As of `r paste0(month(ymd(Sys.Date()), label = TRUE), ". ", day(ymd(Sys.Date())), ", ", year(ymd(Sys.Date())))`, the total number of citations to my work is `r prettyNum(sum(citations_scholar$cites), big.mark = ",")`, my $h$-index is `r as.character(h_index)` and my $i10$-index is `r as.character(i10_index)`, meaning that `r as.character(i10_index)` of my publications have been cited 10 times or more (source: Google Scholar).
* A 2024 global bibliometric analysis by [Research.com](https://research.com/scientists-rankings/social-sciences-and-humanities/ca) of the most influential scholars in the social sciences and humanities (about 16,000 researchers) places me in the **top 3%** of scholars in the world. 
<!-- Ranked 1904 of 16,000 (12%), and the 16,000 are already in the top 2% of scholars according to the Stanford Science Wide Indicators--> 
* In 2024 I was recognized with the **Edward L. Ullman Award** of the Association of American Geographers for lifelong commitment and contributions to the field of transportation geography.
* In 2010 a research team I led was recognized with the **Meredith F. Burrill Award** of the Association of American Geographers for exceptional work at the intersection of policy and basic research in geography.

# Education

```{r education-details}
read_csv(paste0(here(),"/assets/education.csv")) |> 
  detailed_entries(what = Degree, 
                   when = Year, 
                   with = Institution,
                   where = Where, 
                   why = Thesis,
                   .protect = FALSE)
```

# Current Status at McMaster

Full Professor in the School of Earth, Environment and Society since 2014. Tenured since 2007.

# Employment History

## Academic

```{r employment-details}
read_csv(paste0(here(),"/assets/employment.csv")) |> 
  slice_head(n = 4) |>
  detailed_entries(what = Position, 
                   when = Year, 
                   with = Organization,
                   where = Where,
                   .protect = FALSE)
```

## Industry
<!--
Surveyor and construction site supervisor (August 1993 - March 1995) Topographical
survey projects in Nuevo León, Mexico, sponsored by various Municipal Public Works Departments (Monterrey, Guadalupe, Santa Catarina), and by Mercedes-Benz.
-->

Consultant (2015 - present) Environics Analytics, Toronto, Canada. 

# Honours

## Scientific Awards

```{r scientific-awards-details}
read_csv(paste0(here(),"/assets/honors.csv")) |>
  dplyr::filter(Type == "Scientific Awards") |> 
  arrange(desc(Year)) |>
  detailed_entries(what = Organization, 
                   when = Year, 
                   with = Honor,
                   where = Where,
                   why = With,
                   .protect = FALSE)
```

## Visiting Professorships

```{r professorship-details}
read_csv(paste0(here(),"/assets/honors.csv")) |>
  dplyr::filter(Type == "Professorship") |> 
  arrange(desc(Year)) |>
  detailed_entries(what = Honor, 
                   when = Year, 
                   with = Organization,
                   where = Where,
                   .protect = FALSE)
```

## Scholarships

```{r scholarships-details}
read_csv(paste0(here(),"/assets/honors.csv")) |>
  dplyr::filter(Type == "Scholarship") |>  
  arrange(desc(Year)) |>
  detailed_entries(what = Honor, 
                   when = Year, 
                   with = Organization,
                   where = Where,
                   .protect = FALSE)
```

## Trainee Honours

```{r trainee-honors-details}
read_csv(paste0(here(),"/assets/honors.csv")) |>
  dplyr::filter(Type == "Trainee") |> 
  detailed_entries(what = Organization, 
                   when = Year, 
                   with = With,
                   where = Honor,
                   .protect = FALSE)
```

# Editorial

## Editorships

```{r editor-details}
read_csv(paste0(here(),"/assets/editorial-board.csv")) |>
  filter(What == "Editor-in-Chief") |>
  detailed_entries(what = Journal, 
                   where = Year,
                   with = What,
                   .protect = FALSE)
```

```{r associate-editor-details}
read_csv(paste0(here(),"/assets/editorial-board.csv")) |>
  filter(What == "Associate Editor") |>
  detailed_entries(what = Journal, 
                   where = Year,
                   with = What,
                   .protect = FALSE)
```

## Guest Editorships

```{r guest-editor-details}
read_csv(paste0(here(),"/assets/editorial-board.csv")) |>
  filter(What == "Guest Editor") |>
  detailed_entries(what = Editors, 
                   when = Year,
                   with = What,
                   where = glue::glue("{Journal} {Volume}"),
                   why = Title,
                   .protect = FALSE)
```

## Editorial Boards

```{r editorial-board-details}
read_csv(paste0(here(),"/assets/editorial-board.csv")) |>
  filter(What == "Editorial Board Member") |>
  detailed_entries(what = Journal, 
                   where = Year,
                   with = What,
                   .protect = FALSE)
```

# Scholarly and Professional Activities

## Journal Referee

```{r journal-referee}
referee <- read_csv(paste0(here(),"/assets/paper-reviews.csv")) |> 
  pivot_longer(-Journal, 
               names_to = "Year", 
               values_to = "Reviews")
```

### Number of Total Lifetime Reviews

`r sum(referee$Reviews)`

### Number of Reviews in `r current_year`

`r referee |> filter(Year == current_year) |> pull(Reviews) |> sum()`

### Reviews-to-Publications per Year

Fig. \ref{fig:reviews-pubs} is a summary of journal reviews and publications per year. This is an indicator of my contributions to peer-reviewing relative to the demands my submissions put on peer-reviewers.

```{r reviews-per-year, include=FALSE, fig.cap="\\label{fig:reviews-annual-summary}Number of journal reviews per year"}
referee |>
  group_by(Year) |>
  summarize(Reviews = sum(Reviews),
            .groups = "drop") |>
  ggplot() +
  geom_col(aes(x = Year, y = Reviews)) +
  ggthemes::theme_tufte() +
  theme(axis.text = element_text(angle = 45))
```

```{r review-to-publication, fig.cap="\\label{fig:reviews-pubs}Reviews-to-publications by year"}
# Check publication vs. review activity
df_pubs <- bibliography_entries(paste0(here(),"/assets/refereed-publications.bib"))
df_pubs <- data.frame(Year = df_pubs$issued |> 
                        unlist()) |>
  group_by(Year) |>
  summarize(items = n(),
            .groups = "drop") |>
  mutate(type = "Publication")

df_referee <- referee |>
  group_by(Year) |>
  summarize(items = sum(Reviews),
            .groups = "drop") |>
  mutate(type = "Paper Review")

rbind(df_pubs,
      df_referee) |>
  ggplot() +
  geom_col(aes(x = Year,
               y = items,
               fill = type),
           color = "black",
           position = position_dodge(preserve = "single")) +
  scale_fill_manual(values = c("Publication" = "white", "Paper Review" = "black")) +
  ggthemes::theme_tufte() +
  theme(axis.text.x = element_text(angle = 45),
        legend.title = element_blank())
```

### Reviews per journal

```{r journal-referee-details}
referee |>
  group_by(Journal) |> 
  summarize(Reviews = sum(Reviews), 
            .groups = "drop") |>
  detailed_entries(what = Journal, 
                   when = Reviews,
                   .protect = FALSE)
```

# Grant Reviews

```{r}
read_csv(paste0(here(),"/assets/grant-reviews.csv")) |> 
  arrange(desc(Year)) |>
  detailed_entries(what = Role, 
                   when = glue::glue("Number of reviews: {Number}"), 
                   with = glue::glue("{Funder} ({Where})"),
                   where = Year,
                   .protect = FALSE)
```


# Areas of Interest

Transportation; accessibility; equity; justice; spatial data analysis and statistics; transportation modeling; travel behavior; health geography; Geographic Information Systems; Open Science; Open Educational Resources.


# Teaching at a Glance

```{r read-courses-asset}
courses <- read_csv(paste0(here(),"/assets/courses-taught.csv")) 
```

## Total number of courses taught

`r paste0("Undergraduate: ", courses |> filter(Level == "Undergraduate") |> nrow())`

`r paste0("Graduate: ", courses |> filter(Level == "Graduate") |> nrow())`

## Total number of students

`r paste0("Undergraduate: ", courses |> filter(Level == "Undergraduate") |> pull(Enrolment) |> sum() |> prettyNum(big.mark = ","))`

`r paste0("Graduate: ", courses |> filter(Level == "Graduate") |> pull(Enrolment) |> sum() |> prettyNum(big.mark = ","))`

# Teaching (Details)

## Undergraduate Teaching

```{r courses-brief-undergraduate}
courses <- read_csv(paste0(here(),"/assets/courses-taught.csv")) 

courses_summary <- courses |>
  group_by(Code) |> 
  summarize(Name = first(Name), 
            offerings = n(),
            total_students = sum(Enrolment), 
            level = first(Level)) |> 
  arrange(level)

courses_summary |>
  filter(level == "Undergraduate") |>
  detailed_entries(what = glue::glue("Total enrolment: {total_students} students"), 
                   with = Name,
                   where = glue::glue("Times offered: {offerings}"),
                   when = Code,
                   .protect = FALSE)
```

## Graduate Teaching

```{r courses-brief-graduate}
courses_summary |>
  filter(level == "Graduate") |>
  detailed_entries(what = glue::glue("Total enrolment: {total_students} students"), 
                   with = Name,
                   where = glue::glue("Times offered: {offerings}"),
                   when = Code,
                   .protect = FALSE)
```

## Diploma-Certificate Teaching

```{r courses-brief-diploma}
courses_summary |>
  filter(level == "Diploma-Certificate") |>
  detailed_entries(what = glue::glue("Total enrolment: {total_students} students"), 
                   with = Name,
                   where = glue::glue("Times offered: {offerings}"),
                   when = Code,
                   .protect = FALSE)
```


# Training of Highly Qualified Personnel

## Supervision at a Glance

```{r supervisorhip}
supervision <- read_csv(paste0(here(),"/assets/supervision.csv")) 
```

```{r supervision-at-a-glance}
supervision |>
  filter(is.na(With), Status != "Withdrew from Program") |>
  group_by(Level, Program) |>
  summarize(Supervision = n(),
            .groups = "drop") |>
  full_join(supervision |>
              filter(!is.na(With), Status != "Withdrew from Program") |>
              group_by(Level, Program) |>
              summarize(Cosupervision = n(),
                        .groups = "drop"),
            by = c("Level", "Program")) |>
  full_join(supervision |>
              filter(Status == "Withdrew from Program") |>
              group_by(Level, Program) |>
              summarize(Withdrew = n(),
                        .groups = "drop"),
            by = c("Level", "Program")) |>
  arrange(Level) |>
  mutate(Supervision = as.character(Supervision),
         Cosupervision = as.character(Cosupervision),
         Withdrew = as.character(Withdrew)) |>
  replace_na(list(Supervision = "-",
                  Cosupervision = "-",
                  Withdrew = "-")) |>
  gt() |>
  cols_label(Supervision = "Sole Supervisor",
             Cosupervision = "Co-supervisor",
             Withdrew = "Withdrawn from Program") |>
    as_latex()
```


## Undergraduate Supervision

```{r supervisorship-undergraduate}
supervision |>
  filter(Level == "Undergraduate") |>
  arrange(desc(Year), Program) |>
  detailed_entries(what = ifelse(!is.na(With), glue::glue("Co-supervised with {With}"), ""), 
                   with = glue::glue("{Name} ({Institution}, {Country})"),
                   where = case_when(Status == "Complete" ~ as.character(Year),
                                     Status == "In Progress" ~ "In Progress",
                                     Status == "Withdrew from Program" ~ "Withdrew from Program"),
                   when = Program,
                   .protect = FALSE)
```

## Master's Supervision

```{r supervisorship-masters}
supervision |>
  filter(Level == "Master") |>
  arrange(desc(Year)) |>
  detailed_entries(what = ifelse(!is.na(With), glue::glue("Co-supervised with {With}"), ""),
                   with = glue::glue("{Name} ({Institution}, {Country})"),
                   where = case_when(Status == "Complete" ~ as.character(Year),
                                     Status == "In Progress" ~ "In Progress",
                                     Status == "Withdrew from Program" ~ "Withdrew from Program"),
                   when = Program,
                   .protect = FALSE)
```

## Doctoral Supervision

```{r supervisorship-doctoral}
supervision |>
  filter(Level == "Doctoral") |>
  arrange(desc(Year)) |>
  detailed_entries(what = ifelse(!is.na(With), glue::glue("Co-supervised with {With}"), ""), 
                   with = glue::glue("{Name} ({Institution}, {Country})"),
                   where = case_when(Status == "Complete" ~ as.character(Year),
                                     Status == "In Progress" ~ "In Progress",
                                     Status == "Withdrew from Program" ~ "Withdrew from Program"),
                   when = Program,
                   .protect = FALSE)
```


# Supervisory Committees (All are doctoral unless otherwise noted)

Ricardo Lourenco Barros (McMaster University; 2022-) Understanding vegetation dynamics with satellite observations and Explainable Artificial Intelligence (XAI)

Samira Hamidetehrani (McMaster University; 2020-2024) User Preferences and Intentions Regarding Shared Automated Vehicles in Canadian Metropolitan Areas 

Christina Borowiec (McMaster University; Dropped out of program) Active travel

Shaila Jamal (McMaster University; 2023) Generational differences in travel behavior 

Jeremy Gabriel (McMaster University; 2023) Strata analysis

Elnaz Abotalebi (McMaster University; 2019) Consumer stated preferences survey for electric cars

Wade Genders (McMaster University; 2018) Deep Reinforcement Learning Adaptive Traffic Signal Control 

Randy Bui (McMaster University; withdrew from program) Understanding Network Robustness and Critical Roadway Links in the Greater Toronto and Hamilton Area under Short-Term Disruption

Nazila Roofigari-Esfahan (McMaster University; 2016) A Framework for Spatio-Temporal Uncertainty-Aware Scheduling and Control of Linear Projects

Arash Olia (McMaster University; 2016) Modelling and Assessment of the Transportation Potential and Impacts of Connected and Automated Vehicles

Chris Higgins (McMaster University; 2015) A Value Planning Framework for Predicting and
Recapturing the Value of Rapid Transit Infrastructure

Matthew Adams (McMaster University; 2015) Advancing the use of mobile monitoring data for air pollution modelling

Scott Bennett (McMaster University; 2015) Safer walking routes to school: applied and methodological geographies of child pedestrian injury

Sarah Dickin (McMaster University; September 2014) Mapping vulnerability to water-related infectious disease: an ecosystem approach 

Ron Dalumpines (McMaster University; July 2014) Route choice analysis in time-geographic perspective

Kathleen Deutsch (University of California Santa Barbara; June 2013) Sense of place and travel behavior

Andrew Clarke (McMaster University; January 2013) Understanding determinants of active travel

Xudong Liu (McMaster University; withdrew from program in 2011) Integrating firmography in urban models

Jia Yang (McMaster University; withdrew from program in 2011) Modeling firm survival

Renilson Rodriguez da Silva (Universidade de Sao Paulo; completed: March 2011) Accessibility and development in the Amazon region (with Danilo Igliori)

Jamie E.L. Spinney (McMaster University; completed: September 2010) Geography, Land Values, and Municipal Taxation: A Spatial Paradigm for the Estimation and Reclamation of Rent

Kelsey MacCormack (McMaster University; completed: July 2010) Delineation of subsurface gravel units beneath the Dundas Valley, Ontario

Theodora Pouliou (McMaster University; completed: September 2009) Individual and Socio-Environmental Determinants of Obesity in Canada

Hejun Kang (McMaster University; completed: August 2008) Intra-households interactions and travel behavior

Dimitris Potoglou (McMaster University; completed: April 2006) Potential demand for alternative fuelled vehicles in the City of Hamilton CMA


# Examination Committees

Samira Hamidetehrani (Ph.D., McMaster University; School of Earth, Environment and Society ) September 15, 2023

Daniel Van Veghel (M.Sc., McMaster University; School of Earth, Environment and Society ) August 28, 2023

Bruno Dias dos Santos (M.Sc., INPE, Brazil) May 18, 2023

Daniela Arias Molinares (Ph.D., Facultad de Geografía e Historia, Universidad Complutense de Madrid) May 10, 2023

Shaila Jamal (Ph.D. McMaster University; School of Earth, Environment and Society) May 9, 2023

Lucy Joseph Chabariko (Ph.D., School of Transportation Sciences, University of Hasselt) December 21, 2020

Darcy Reynard (Ph.D., Department of Earth and Atmospheric Sciences, University of Alberta) December 18, 2020

Jose Carpio-Pinedo (Ph.D., ETS Arquitectura, Universidad Politecnica de Madrid) November 19, 2020

Sami Kurani (M.A., McMaster University; School of Earth, Environment and Society) September 28, 2020

Geun (Jayden) Choi (M.A., McMaster University; School of Earth, Environment and Society) August 25, 2020

Matthew Brown (M.A., McMaster University; School of Earth, Environment and Society) April 3, 2020

Javier Delso (Ph.D., ETSI Montes, Universidad Politecnica de Madrid) February 25, 2020

Shaila Jamal (Ph.D., Comprehensive Examination, School of Geography and Earth Sciences) February 11, 2020

Kyran Cupido (Ph.D., Arizona State University, School of Mathematics and Statistical Sciences) December 6, 2019

Zoha Anjum (MPH, McMaster University, Health Research Methods, Evidence, and Impact) September 2019

Georgios Sarlas (Ph.D., ETH Zurich, Civil, Environmental, and Geomatics Engineering) July 1, 2019

Matthew Quick (Ph.D., University of Waterloo; School of Planning) April 24, 2019

Wade Genders (Ph.D., McMaster University; Civil Engineering) November 22, 2018

Quinn Hachey (M.A., McMaster University; School of Geography and Earth Sciences) December 18, 2017

Wei Lu (M.A., McMaster University; School of Geography and Earth Sciences) September 28, 2017

Charles Burke (Ph.D., McMaster University; School of Geography and Earth Sciences) December 5, 2016

Nazila Roofigari-Esfahan (Ph.D., McMaster University; Civil Engineering) August 8, 2016

Juan Pablo Ospina Zapata (Ph.D., Comprehensive Examination. Universidad Nacional de Colombia – Medellin; Civil Engineering) June 10, 2016

Arash Olia (Ph.D., McMaster University; Civil Engineering) June 8, 2016

Geraldine Fuenmayor (Ph.D., University of Calgary; Civil Engineering) May 19, 2016

Sadia Yawar (M.A., McMaster University; School of Geography and Earth Sciences) April 29, 2016

An Neven (Ph.D., Hasselt University; School of Transportation Sciences) September 7, 2015

Chris Higgins (Ph.D., McMaster University; School of Geography and Earth Sciences) August 28, 2015

Matthew Adams (Ph.D., McMaster University; School of Geography and Earth Sciences) July 31, 2015

Scott Bennett (Ph.D., McMaster University; School of Geography and Earth Sciences) July 3, 2015

Wade Genders (M.A.Sc., McMaster University; Civil Engineering) November 17, 2014

Sarah Dickin (Ph.D., McMaster University; Geography) September 5, 2014

Simon Minelli (M.A.Sc., McMaster University; Civil Engineering) September 3, 2014

Ron Dalumpines (Ph.D., McMaster University; Geography) July 28, 2014

Markus Botte (Ph.D., University of Western Australia; Business) July 4, 2014

Kathleen Deutsch (Ph.D., University of California Santa Barbara; Geography) June 20, 2013

Chris Higgins (Ph.D., Comprehensive Examination. McMaster University; Geography and Earth Sciences) February 14, 2013

Andrew Clarke (Ph.D., McMaster University; Geography and Earth Sciences) September 24, 2012

Adrian Klisz (M.A., McMaster University; Geography and Earth Sciences) July 24, 2012

Sarah Dickin (Ph.D., Comprehensive Examination. McMaster University; Geography and Earth Sciences) October 24, 2011

Jia Yang (M.A., McMaster University; Geography and Earth Sciences) September 12, 2011

Xudong Liu (M.A., McMaster University; Geography and Earth Sciences) September 12, 2011 

Ron Dalumpines (Ph.D., Comprehensive Examination. McMaster University; Geography and Earth Sciences) December 3, 2010 

Jia Yang (Ph.D., Comprehensive Examination. McMaster University; Geography and Earth Sciences) December 2, 2010

Xudong Liu (Ph.D., Comprehensive Examination. McMaster University; Geography and Earth Sciences) December 2, 2010 

Jamie E.L. Spinney (Ph.D., McMaster University; Geography and Earth Sciences) September 24, 2010

Kelsey McCormack (Ph.D., McMaster University; Geography and Earth Sciences) July 27, 2010

PJ Saberton (M.A., McMaster University; Geography and Earth Sciences) July 26, 2010

Adam Drackley (M.A., McMaster University; Geography and Earth Sciences) July 26, 2010

Kathleen Deutsch (Ph.D., Proposal Defense. University of California Santa Barbara) April 14, 2010

Daniela Schettini (Ph.D., Universidade de São Paulo; Economics) April 9, 2010

Ana Maria Bonomi Barufi (M.A., Universidade de São Paulo; Economics) February 12, 2010

Logan McLeod (Ph.D., McMaster University; Economics) November 13, 2009

Yifei Wang (M.A., McMaster University; Geography and Earth Sciences) September 18, 2009

Ivy Dam (M.A., McMaster University; Geography and Earth Sciences) September 18, 2009

Karen Wiley (M.A., McMaster University; Geography and Earth Sciences) September 10, 2009

Theodora Pouliou (Ph.D., McMaster University; Geography and Earth Sciences) September 8, 2009

Terry Li (Ph.D., The University of Queensland; School of Geography, Planning and Environmental Management) August, 2009

Gustavo Renno Rocha (M.Sc., Qualification Examination. Universidade de São Paulo; Escola de Engenharia de São Carlos) August 7, 2009

Dan Harrington (Ph.D., Comprehensive Examination. McMaster University; Geography and Earth Sciences) January 20, 2009

Kelsey MacCormack (Ph.D., Comprehensive Examination. McMaster University; Geography and Earth Sciences) September 22, 2008

Hejun Kang (Ph.D., McMaster University; Geography and Earth Sciences) August18, 2008

Kenneth Harold Doust (Ph.D., University of New South Wales, Australia; School of Civil and Environmental Engineering) May, 2008

Sylvia He (M.A., McMaster University; Geography and Earth Sciences) August 8, 2006

Jennifer L. Campos (Ph.D., McMaster University; Psychology and Neuroscience) September 11, 2007

Jessica Becker (M.A., McMaster University; Geography and Earth Sciences) September 17, 2007

Charles Cheung (Ph.D., University of New South Wales, Australia; School of Civil and Environmental Engineering) June, 2005


# Research and Other Funding

## Funding at a Glance

```{r research-funding}
research_funding <- read_csv(paste0(here(),"/assets/research-funding.csv")) |>
  mutate(Amount_num = str_replace_all(Amount, ",", ""),
         Amount_num = str_extract_all(Amount_num, "\\d+") |>
           as.numeric(),
         Share = Amount_num * Share,
         Share_chr = prettyNum(Share, big.mark =",", digits = 4),
         Share_chr = paste0("$", Share_chr))
```

The funding total of all projects that I have been part of is `r paste0("CAD ", prettyNum(sum(research_funding$Amount_num), big.mark = ",", digits = 4))`. The total in research grants from various organizations, including the Canadian Institutes of Health Research (CIHR), the Natural Sciences and Engineering Research Council of Canada (NSERC), and the Social Sciences and Humanities Research Council of Canada (SSHRC) is `r paste0("CAD ", prettyNum(sum(research_funding$Amount_num[research_funding$Purpose == "Research"]), big.mark = ",", digits = 4))`. I have also been the recipient of several grants to improve teaching practice, to the total of `r paste0("CAD ", prettyNum(sum(research_funding$Amount_num[research_funding$Purpose == "Teaching"]), big.mark = ",", digits = 4))`. And, I have received numerous travel grants, amounting to `r paste0("CAD ", prettyNum(sum(research_funding$Amount_num[research_funding$Purpose == "Travel"]), big.mark = ",", digits = 4))`.

My personal share of these funds to date amounts to `r paste0("CAD ", prettyNum(sum(research_funding$Share), big.mark = ",", digits = 4))`. The distribution of these funds for research, teaching, and travel, and from various organizations, can be seen in Fig. \ref{fig:research-funding-share}.

```{r research-funding-plot, out.width="0.7\\linewidth", fig.cap="\\label{fig:research-funding-share}My share of research funds by source"}
ggplot(research_funding, 
       aes(area = Share, 
           fill = Purpose,
           subgroup = Funder_Short,
           label = Share_chr)) +
  geom_treemap() +
  geom_treemap_subgroup_border() +
  geom_treemap_subgroup_text(place = "centre", grow = T, alpha = 0.25, 
                             colour =
                             "black", fontface = "italic", min.size = 0) +
  geom_treemap_text(colour = "white", place = "topleft", reflow = T) +
  scale_fill_manual(values = c("Research" = "deepskyblue", "Teaching" = "darkorange", "Travel" = "darkolivegreen3")) +
  theme(legend.position = "bottom")
```

## Detailed Funding

```{r research-funding-details}
read_csv(paste0(here(),"/assets/research-funding.csv")) |>
  arrange(desc(Year)) |>
  detailed_entries(what = Title, 
                   when = Year, 
                   where = Amount,
                   with = glue::glue("{Funder}, {Where}"),
                   why = glue::glue("PI: {PI}; team size: {Participants} researchers"),
                   .protect = FALSE)
```

# Research Impact

```{r summary-bibliography, include=FALSE}
books <- bibliography_entries(paste0(here(),"/assets/books.bib")) |>
  arrange(desc(issued), desc(author$family))

books_authors <- csl_name(books)
books_authors <- books_authors$family$author
books_authors <- books_authors$family
n_authors <- str_split(books_authors, ",") |>
           lapply(length) |>
           unlist()

summary_books <- books |>
  mutate(n_authors = n_authors,
         first_author = str_split_i(books_authors, ",", 1),
         second_author = str_split_i(books_authors, ",", 2),
         senior_author = str_split_i(books_authors, ",", -1),
         case_author = case_when(n_authors == 1 ~ "single",
                                 n_authors >= 2 & str_detect(second_author, "Páez") ~ "second",
                                 n_authors > 1 & str_detect(first_author, "Páez") ~ "first",
                                 n_authors > 2 & str_detect(senior_author, "Páez") ~ "senior",
                                 TRUE ~ "other")) |> select(ends_with("author")) |>
  summarize(type = "Books",
            total = n(),
            mean_authors = round(mean(n_authors), 2),
            max_authors = max(n_authors),
            single_author = glue(sum(case_author == "single"), " (", round(sum(case_author == "single")/n(), 2) * 100, "%)"),
            first_author = glue(sum(case_author == "first"), " (", round(sum(case_author == "first")/n(), 2) * 100, "%)"),
            second_author = glue(sum(case_author == "second"), " (", round(sum(case_author == "second")/n(), 2) * 100, "%)"),
            senior_author = glue(sum(case_author == "senior"), " (", round(sum(case_author == "senior")/n(), 2) * 100, "%)"),
            other_author = glue(sum(case_author == "other"), " (", round(sum(case_author == "other")/n(), 2) * 100, "%)"))

edited_books <- bibliography_entries(paste0(here(),"/assets/edited-books.bib")) |>
  #bibliography_entries(paste0(here(),"/assets/savedrecs_2.bib")) |>
  arrange(desc(issued), desc(author$family))


book_chapters <- bibliography_entries(paste0(here(),"/assets/book-chapters.bib")) |>
  #bibliography_entries(paste0(here(),"/assets/savedrecs_2.bib")) |>
  arrange(desc(issued), desc(author$family))

book_chapters_authors <- csl_name(book_chapters)
book_chapters_authors <- book_chapters_authors$family$author
book_chapters_authors <- book_chapters_authors$family
n_authors <- str_split(book_chapters_authors, ",") |>
           lapply(length) |>
           unlist()

summary_book_chapters <- book_chapters |>
  mutate(n_authors = n_authors,
         first_author = str_split_i(book_chapters_authors, ",", 1),
         second_author = str_split_i(book_chapters_authors, ",", 2),
         senior_author = str_split_i(book_chapters_authors, ",", -1),
         case_author = case_when(n_authors == 1 ~ "single",
                                 n_authors >= 2 & str_detect(second_author, "Páez") ~ "second",
                                 n_authors > 1 & str_detect(first_author, "Páez") ~ "first",
                                 n_authors > 2 & str_detect(senior_author, "Páez") ~ "senior",
                                 TRUE ~ "other")) |> select(ends_with("author")) |>
  summarize(type = "Book chapters",
            total = n(),
            mean_authors = round(mean(n_authors), 2),
            max_authors = max(n_authors),
            single_author = glue(sum(case_author == "single"), " (", round(sum(case_author == "single")/n(), 2) * 100, "%)"),
            first_author = glue(sum(case_author == "first"), " (", round(sum(case_author == "first")/n(), 2) * 100, "%)"),
            second_author = glue(sum(case_author == "second"), " (", round(sum(case_author == "second")/n() * 100, 2), "%)"),
            senior_author = glue(sum(case_author == "senior"), " (", round(sum(case_author == "senior")/n() * 100, 2), "%)"),
            other_author = glue(sum(case_author == "other"), " (", round(sum(case_author == "other")/n(), 2), "%)"))

peer_reviewed_articles <- bibliography_entries(paste0(here(),"/assets/refereed-publications.bib")) |>
  arrange(desc(issued), desc(author$family))

peer_reviewed_articles_authors <- csl_name(peer_reviewed_articles)
peer_reviewed_articles_authors <- peer_reviewed_articles_authors$family$author
peer_reviewed_articles_authors <- peer_reviewed_articles_authors$family

n_authors <- str_split(peer_reviewed_articles_authors, ",") |>
           lapply(length) |>
           unlist()

summary_peer_reviewed_articles <- peer_reviewed_articles |>
  cbind(n_authors) |>
  mutate(first_author = str_split_i(peer_reviewed_articles_authors, ",", 1),
         second_author = str_split_i(peer_reviewed_articles_authors, ",", 2),
         senior_author = str_split_i(peer_reviewed_articles_authors, ",", -1),
         case_author = case_when(n_authors == 1 ~ "single",
                                 n_authors >= 2 & str_detect(second_author, "Páez") ~ "second",
                                 n_authors > 1 & str_detect(first_author, "Páez") ~ "first",
                                 n_authors > 2 & str_detect(senior_author, "Páez") ~ "senior",
                                 TRUE ~ "other")) |> select(ends_with("author")) |>
  summarize(type = "Peer reviewed articles",
            total = n(),
            mean_authors = round(mean(n_authors), 2),
            max_authors = max(n_authors),
            single_author = glue(sum(case_author == "single"), " (", round(sum(case_author == "single")/n(), 2) * 100, "%)"),
            first_author = glue(sum(case_author == "first"), " (", round(sum(case_author == "first")/n(), 2) * 100, "%)"),
            second_author = glue(sum(case_author == "second"), " (", round(sum(case_author == "second")/n(), 2) * 100, "%)"),
            senior_author = glue(sum(case_author == "senior"), " (", round(sum(case_author == "senior")/n(), 2) * 100, "%)"),
            other_author = glue(sum(case_author == "other"), " (", round(sum(case_author == "other")/n(), 2) * 100, "%)"))

peer_reviewed_conference <- bibliography_entries(paste0(here(),"/assets/conference-presentations-peer-reviewed.bib")) |>
  arrange(desc(issued), desc(author$family))

peer_reviewed_conference_authors <- csl_name(peer_reviewed_conference)
peer_reviewed_conference_authors <- peer_reviewed_conference_authors$family$author
peer_reviewed_conference_authors <- peer_reviewed_conference_authors$family

n_authors <- str_split(peer_reviewed_conference_authors, ",") |>
           lapply(length) |>
           unlist()

summary_peer_reviewed_conference <- peer_reviewed_conference |>
  cbind(n_authors) |>
  mutate(first_author = str_split_i(peer_reviewed_conference_authors, ",", 1),
         second_author = str_split_i(peer_reviewed_conference_authors, ",", 2),
         senior_author = str_split_i(peer_reviewed_conference_authors, ",", -1),
         case_author = case_when(n_authors == 1 ~ "single",
                                 n_authors >= 2 & str_detect(second_author, "Páez") ~ "second",
                                 n_authors > 1 & str_detect(first_author, "Páez") ~ "first",
                                 n_authors > 2 & str_detect(senior_author, "Páez") ~ "senior",
                                 TRUE ~ "other")) |> select(ends_with("author")) |>
  summarize(type = "Peer reviewed conference presentations",
            total = n(),
            mean_authors = round(mean(n_authors), 2),
            max_authors = max(n_authors),
            single_author = glue(sum(case_author == "single"), " (", round(sum(case_author == "single")/n(), 2) * 100, "%)"),
            first_author = glue(sum(case_author == "first"), " (", round(sum(case_author == "first")/n(), 2) * 100, "%)"),
            second_author = glue(sum(case_author == "second"), " (", round(sum(case_author == "second")/n(), 2) * 100, "%)"),
            senior_author = glue(sum(case_author == "senior"), " (", round(sum(case_author == "senior")/n(), 2) * 100, "%)"),
            other_author = glue(sum(case_author == "other"), " (", round(sum(case_author == "other")/n(), 2) * 100, "%)"))

bibliography_glance <- rbind(summary_books,
                             summary_book_chapters,
                             summary_peer_reviewed_articles,
                             summary_peer_reviewed_conference)
```

```{r citations-by-category}
citation_categories <- read_delim(glue(here(), "/assets/wos_cited_fields_2024_09_17.txt")) |>
  transmute(Category = `Web of Science Categories`,
            Count = `Record Count`) |>
  mutate(super_category = case_when(str_detect(Category, "Transport") ~ "Transportation",
                                    str_detect(Category, "Environmental") ~ "Environmental Science/Studies",
                                    TRUE ~ Category)) |>
  group_by(super_category) |>
  summarize(Category = first(super_category),
            Count = sum(Count),
            .groups = "drop") |>
  arrange(desc(Count)) |>
  slice_head(n = 12)
```

```{r citations-by-country}
citation_countries <- read_delim(glue(here(), "/assets/wos_cited_countries_2024_09_17.txt")) |>
  transmute(Country = `Countries/Regions`,
            Count = `Record Count`) |>
  mutate(Country = str_to_title(Country),
         Country = case_when(str_detect(Country, "Peoples R China") ~ "China",
                             str_detect(Country, "Usa") ~ "United States",
                             TRUE ~ Country)) |>
  arrange(desc(Count)) |>
  slice_head(n = 12)
```
```{r citations-by-sdg}
citation_sdg <- read_delim(glue(here(), "/assets/wos_cited_sdg_2024_09_17.txt"),
                           delim = "\t") |>
  transmute(Goal = `Sustainable Development Goals`,
            Count = as.numeric(`Record Count`)) |>
  arrange(desc(Count)) |>
  slice_head(n = 12)
```

Fig. \ref{fig:citations} gives a summary of my research impact according to Google Scholar. As of `r lubridate::month(Sys.Date(), label = TRUE) |> as.character()`, `r lubridate::year(Sys.Date()) |> as.character()`, my research has been cited a total of `r prettyNum(get_profile(id)$total_cites, big.mark = ",")` times, and my h-index is `r as.character(h_index)`. The i10-index indicates that `r as.character(i10_index)`, or approximately `r paste0(round(100 * i10_index/sum(bibliography_glance$total)), "%")` of my publications have been cited ten times or more. 

The impact of my work can also be appreciated by the breadth of the fields in which it is cited. According to Web of Science (Fig. \ref{fig:citations-by-field}), my research is cited by scholars in numerous disciplines, notably in  `r citation_categories$super_category[1]`, `r citation_categories$super_category[2]`, `r citation_categories$super_category[3]`, `r citation_categories$super_category[4]`, and `r citation_categories$super_category[5]`. My publications have been cited by researchers in more than 100 countries; as seen in Fig. \ref{fig:citations-by-country}, most citations to my work are by researchers in the `r citation_countries$Country[1]`, `r citation_countries$Country[2]`, `r citation_countries$Country[3]`, `r citation_countries$Country[4]`, and `r citation_countries$Country[5]`.

Lastly, my work has contributed to inform research that aligns with the United Nations Sustainable Development Goals (see Fig. \ref{fig:citations-by-sdg}), particularly goals `r citation_sdg$Goal[1]`, `r citation_sdg$Goal[2]`, `r citation_sdg$Goal[3]`, `r citation_sdg$Goal[4]`, and `r citation_sdg$Goal[5]`.

Combined with the level of funding described above, the cost-effect of my research is approximately `r paste0("CAD ", prettyNum(sum(research_funding$Share)/bibliography_glance$total[3], big.mark = ",", digits = 2))` per peer-reviewed article (not counting book chapters, edited books, or books). To put this number in context, this is equivalent to `r paste0(prettyNum(sum(research_funding$Share)/bibliography_glance$total[3]/13271.94 * 100, big.mark = ",", digits = 2), "%")` of a one-year graduate research assistantship at my institution. In terms of impact, the cost-effect of my research is `r paste0("CAD ", prettyNum(sum(research_funding$Share)/get_profile(id)$total_cites, big.mark = ",", digits = 2))` per citation.

```{r citations-plot, fig.cap="\\label{fig:citations}Citations per year (data from Google Scholar)"}
citations_scholar <- scholar::get_citation_history(id)

citations_scholar |>
  ggplot() + 
  geom_col(aes(x = year, 
               y = cites),
           color = "black",
           fill = "white") + 
  annotate(geom = "text", 
           x = 2004, 
           y = 950, 
           hjust = 0,
           label = paste0("Total cites = ", 
                          prettyNum(get_profile(id)$total_cites, big.mark = ","))) +
  annotate(geom = "text", 
           x = 2004, 
           y = 900, 
           hjust = 0,
           label = paste0("h-index = ", 
                          as.character(h_index))) +
  annotate(geom = "text", 
           x = 2004, 
           y = 850, 
           hjust = 0,
           label = paste0("i10-index = ", 
                          as.character(i10_index))) +
  ggthemes::theme_tufte()
```

```{r citations-field, out.width="0.7\\linewidth", fig.cap="\\label{fig:citations-by-field}Citations by field (data from Web of Science)"}
citation_categories |>
  mutate(label = glue("{super_category} ({Count})")) |>
  ggplot(aes(area = Count, 
             fill = super_category,
             label = label)) +
  geom_treemap() +
  #geom_treemap_subgroup_border() +
  #geom_treemap_subgroup_text(place = "centre", grow = T, alpha = 0.25, 
  #                           colour =
  #                           "black", fontface = "italic", min.size = 0) +
  geom_treemap_text(colour = "black", 
                    place = "topleft",
                    padding.x = grid::unit(2, "mm"),
                    padding.y = grid::unit(2, "mm"), 
                    reflow = T) +
  scale_fill_brewer(palette = "Set3") +
  theme(legend.position = "none")
```

```{r citations-country, out.width="0.7\\linewidth", fig.cap="\\label{fig:citations-by-sdg}Citations by country (data from Web of Science)"}
citation_countries |>
  mutate(label = glue("{Country} ({Count})")) |>
  ggplot(aes(area = Count, 
             fill = Country,
             label = label)) +
  geom_treemap() +
  geom_treemap_text(colour = "black", 
                    place = "topleft",
                    padding.x = grid::unit(2, "mm"),
                    padding.y = grid::unit(2, "mm"), 
                    reflow = T) +
  scale_fill_brewer(palette = "Set3") +
  theme(legend.position = "none")

```

```{r citations-sdg, out.width="0.7\\linewidth", fig.cap="\\label{fig:citations-by-country}Citations by Sustainable Development Goal (data from Web of Science)"}
citation_sdg |>
  mutate(label = glue("{Goal} ({Count})")) |>
  ggplot(aes(area = Count, 
             fill = Goal,
             label = label)) +
  geom_treemap() +
  geom_treemap_text(colour = "black", 
                    place = "topleft",
                    padding.x = grid::unit(2, "mm"),
                    padding.y = grid::unit(2, "mm"), 
                    reflow = T) +
  scale_fill_brewer(palette = "Set3") +
  theme(legend.position = "none")
```

# Policy Impact

```{r policy-impact-preparation}
# Read policy impact file. This was sourced from Overton.io: check this file for instructions: POLICY_IMPACT_README.txt
policy_impact_mac <- read_csv(paste0(here(),"/assets/policy-impact-mcmaster.csv"))
policy_impact_tohoku <- read_csv(paste0(here(),"/assets/policy-impact-tohoku.csv"))

# Read policy impact file. This was sourced from Overton.io: check this file for instructions: POLICY_IMPACT_README.txt
policy_impact_topics <- read_csv(paste0(here(),"/assets/policy-impact-topics.csv"))

# Select topics
policy_impact_topics <- policy_impact_topics |> 
  rename(Subject_area = `Subject area`,
         Document_count = `Document count`,
         Reason_highlighted = `Reason highlighted`) |>
  filter(Subject_area == "All") |>
  filter(!Topic %in% c("Branches of science", "Data", "Research", "Statistics", "Regression analysis", "Dependent and independent variables", "Technology", "Information", "Geographic information system", "Computer network", "Spatial analysis", "International Transport Forum", "Time", "Errors and residuals", "World population", "Canada", "Correlation and dependence", "Database")) |>
  mutate(Topic = ifelse(str_detect(Topic, "Econom"), "Economy/Economics", Topic),
         Topic = ifelse(str_detect(Topic, "rapid transit") | str_detect(Topic, "Rapid transit"), "Bus/Rapid transit", Topic)) |>
  group_by(Topic, Reason_highlighted) |>
  summarize(Document_count = sum(Document_count),
            .groups = "drop")
  

# Load simple features object with world map
world <- ne_countries(scale = "medium", returnclass = "sf")

# Filter out Antarctica
world <- world |>
  filter(continent != "Antarctica")

# Retrieve the country centroids from world map
country_centroids <- world |>
  st_centroid() |>
  select(name, name_long, brk_name, formal_en)

policy_impact <- bind_rows(policy_impact_mac,
                           policy_impact_tohoku) |>
  rename(Source_country = `Source country`,
         Source_type = `Source organisation type`,
         Source_title = `Source title`) |>
  # Fix names of countries
  mutate(Source_country = ifelse(Source_country == "USA",
                                 "United States of America", 
                                 Source_country),
         Source_country = ifelse(Source_country == "UK", 
                                 "United Kingdom",
                                 Source_country)) |>
  mutate(Languages = case_when(Languages == "eng" ~ "English",
                               Languages == "por" ~ "Portuguese",
                               Languages == "swe" ~ "Swedish",
                               Languages == "spa" ~ "Spanish",
                               Languages == "fre" ~ "French",
                               Languages == "est" ~ "Estonian"))

# Join the number of policy documents by country to the country centroids
country_centroids <- country_centroids |>
  left_join(policy_impact |>
              # Plot documents from the EU on Belgium
              mutate(Source_country = ifelse(Source_country == "EU", "Belgium", Source_country)) |>
              group_by(Source_country) |>
              summarize(n_documents = n()),
            by =  c("name" = "Source_country")) |>
  filter(!is.na(n_documents))

# Languages

policy_impact_languages <- policy_impact |> 
  group_by(Languages) |> 
  summarize(n_lang = n(), 
            .groups = "drop")

```

<!-- 
My analysis was done on September 17, 2024. At this time I am in the fourth place on the eight page of the search for McMaster researchers. Since each page is 25 researchers, this means I am in the top 25 * 7 + 4 = 179 most cited researchers. There are 10,000 researchers.

Non-health researchers in the database with more citations:

- John Burbridge (256: social sciences) (Emeritus)
- Lonnie Maggie (236: social sciences) (Emeritus)
- Frank T. Denton (222: Economy, Business, and Finance) (Emeritus)
- Michael R. Veall (222: Social Sciences) (Active)
- Thomas F. Crossley (196: Social Sciences) (No longer at McMaster)
- Chris M. Wood (215: environment) (No longer at McMaster)
- Magdalena Janus (213: education) (Active)
- A. Leslie Robb (184: Social Sciences) (Emeritus)
- Pavlos S. Kanaroglou (172: Economy, Business, and Finance) (Deceased)
- Arthur Sweetman (158: education) (Active)
- Antonio Paez (137: Economy, Business, and Finance)

Analysis updated on November 12, 2024. At this time I am in the 20th place on the eight page of the search for McMaster researchers. Since each page is 25 researchers, this means I am in the top 25 * 7 + 20 = 195 most cited researchers. There are 10,000 researchers.

Non-health researchers in the database with more citations:

- John Burbridge (280: social sciences) (Emeritus)
- Lonnie Maggie (261: social sciences) (Emeritus)
*-* Magdalena Janus (244: education) (Active)
*-* Michael R. Veall (230: Social Sciences) (Active)
- Frank T. Denton (227: Economy, Business, and Finance) (Emeritus)
- Thomas F. Crossley (206: Social Sciences) (No longer at McMaster)
- Chris M. Wood (199: environment) (No longer at McMaster)
- A. Leslie Robb (194: Social Sciences) (Emeritus)
- Dustin Garrick (175L environment) (Not at McMaster)
- Nidhi Nagabhatla (175: environment) (Not at McMaster)
*-* Arthur Sweetman (166: education) (Active)
- Pavlos S. Kanaroglou (166: Economy, Business, and Finance) (Deceased)
- Abigail Payne (154: education) (Not at McMaster)
- Evert Nieboer (152: Economic sector) (Emeritus - Biomedical Sciences)
*-* Eric Duku (149: Education) (Part-time, PBN)
*-* K. Bruce Newbold (148: social sciences)(Active)
*-* Antonio Paez (137: Economy, Business, and Finance)

Analysis updated on January 2 2025. At this time I am in the 25th place on the fifth page of the search for McMaster researchers. Since each page is 25 researchers, this means I am in the top 25 * 4 + 25 = 125 most cited researchers. There are 10,000 researchers.

Non-health researchers in the database with more citations:

- John Burbridge (289: social sciences) (Emeritus) 25 * 3 + 14 = 89
- Lonnie Maggie (270: social sciences) (Emeritus) 25 * 3 + 20 = 95
*-* Magdalena Janus (250: education) (Active) 25 * 4 + 5 = 105
*-* Michael R. Veall (234: Social Sciences) (Active) 25 * 4 + 15 = 115
- Frank T. Denton (230: Economy, Business, and Finance) (Emeritus) 25 * 4 + 17 = 117
- Pavlos S. Kanaroglou (228: Economy, Business, and Finance) (Deceased) 25 * 4 + 20 = 120
*-* Antonio Paez (224: Economy, Business, and Finance) 25 * 4 + 25 = 125
---
- Chris M. Wood (218: environment) (No longer at McMaster) 
*-* Darren M. Scott (207: social sciences)(Active) 25 * 5 + 12 = 137
- Thomas F. Crossley (207: Social Sciences) (No longer at McMaster)
- A. Leslie Robb (202: Social Sciences) (Emeritus) 25 * 5 + 20 = 145
*-* K. Bruce Newbold (194: social sciences)(Active) 25 * 6 + 6 = 156
*-* Arthur Sweetman (170: education) (Active)  25 * 7 + 3  = 178
- Evert Nieboer (163: Economic sector) (Emeritus - Biomedical Sciences) 25 * 7 + 11  = 186
*-* Eric Duku (155: Education) (Part-time, PBN) 25 * 7 + 19 = 194
- Abigail Payne (154: education) (Not at McMaster)
*-* M. Altaf Arain (150: environment)(Active) 25 * 8 + 5 = 205

Analysis updated on March 7 2025. At this time I am in the 7th place on the fifth page of the search for McMaster researchers. Since each page is 25 researchers, this means I am in the top 25 * 4 + 7 = 107 most cited researchers. There are 10,000 researchers.

Non-health researchers in the database with more citations:

- David R. Offord (331: education) (Deceased)
- John Burbridge (298: social sciences) (Emeritus)
- Lonnie Maggie (278: social sciences) (Emeritus)
*-* Magdalena Janus (257: education) (Active)
*-* Antonio Paez (249: Economy, Business, and Finance)
---
- Pavlos S. Kanaroglou (241: Economy, Business, and Finance) (Deceased)
- Frank T. Denton (240: Economy, Business, and Finance) (Emeritus)
*-* Darren M. Scott (238: social sciences)(Active)
*-* Michael R. Veall (238: Social Sciences) (Active)
- Chris M. Wood (232: environment) (No longer at McMaster) 
- Thomas F. Crossley (215: Social Sciences) (No longer at McMaster)
- Janet Ajzentat (213: Politics) (Deceased)
- A. Leslie Robb (207: Social Sciences) (Emeritus)
*-* K. Bruce Newbold (206: social sciences)(Active)
- Evert Nieboer (186: Economic sector) (Emeritus - Biomedical Sciences)
*-* Arthur Sweetman (185: education) (Active)
*-* Eric Duku (164: Education) (Part-time, PBN)
- Abigail Payne (159: education) (Not at McMaster)
- Jim Stanford (156: labour)
*-* M. Altaf Arain (147: environment)(Active)
-->

In addition to the scholarly impact of my research, my work has helped to inform policy. According to an analysis of policy impact using data from [Overton.io](https://www.overton.io)^[Analysis done on November 18, 2024], I am in the top `r round((25 * 4 + 25)/10000 * 100)`% of all researchers at McMaster in terms of citations in policy documents. When we consider active researchers in the social sciences, I rank second at McMaster in terms of citations in policy documents, after Prof. Magdalena Janus (Faculty of Health Sciences).

The impact of my research on policy is reflected in citations in multiple languages, including `r policy_impact_languages$Languages[1]`, `r policy_impact_languages$Languages[2]`, `r policy_impact_languages$Languages[3]`, `r policy_impact_languages$Languages[4]`, and `r policy_impact_languages$Languages[5]`. The international reach of this impact can be appreciated in Fig. \ref{fig:policy-impact-map}, which shows the source countries of documents that cite my work. These countries include Canada, US, Mexico, Brazil, several European countries, Australia, and New Zealand. Besides governments at various levels in said countries, numerous Inter-governmental Organizations (IGOs) also refer to my work in their policy documents, including the European Union, OECD, the World Health Organization, the Pan American Health Organization, the World Bank, the Inter-American Development Bank, the International Transport Forum, and the Global Commission on the Economy and Climate. Think tanks that cite my research in policy documents include [IPEA](https://www.ipea.gov.br/forumbrics/en/) (Brazil), the [Lincoln Institute](https://www.lincolninst.edu) (US), [MOTU](https://www.motu.nz) (New Zealand), and [DIW](https://www.diw.de/en) (Germany).

```{r policy-impact-map, fig.cap="\\label{fig:policy-impact-map}Countries where policy documents reference my research"}
ggplot() +
  geom_sf(data = world) +
  geom_sf(data = country_centroids, 
          aes(size = n_documents)) +
  labs(caption = "Data source: Overton.io") +
  scale_size_continuous(range = c(1, 8)) +
  theme_void() +
  theme(legend.position = "none")
```

The distribution of citations in policy documents is more or less evenly distributed between governments and Inter-governmental Organizations, followed by think tanks, as seen in Fig. \ref{fig:policy-impact-sources}.

```{r policy-impact-plot, out.width="0.7\\linewidth", fig.cap="\\label{fig:policy-impact-sources}Policy sources that cite my research"}

policy_impact |> 
  group_by(Source_type, 
           Source_title) |> 
  summarize(n = n(),
            .groups = "drop") |>
  # mutate(Source_type = case_when(Source_type == "government" ~ "Government",
  #                                Source_type == "igo" ~ "IGO",
  #                                Source_type == "think tank" ~ "Think Tank",
  #                                Source_type == "other" ~ "Other")) |>
  drop_na() |>
  ggplot(aes(area = n, 
           fill = Source_type,
           subgroup = Source_type,
           subgroup2 = Source_title,
           label = Source_title)) +
  geom_treemap() +
  geom_treemap_subgroup_border(color = "white") +
  geom_treemap_subgroup2_border(color = "white", size = 1) +
  # geom_treemap_subgroup_text(place = "centre", grow = T, alpha = 0.25, 
  #                            colour =
  #                            "black", fontface = "italic", min.size = 0) +
  geom_treemap_text(colour = "white", place = "topleft", reflow = T) +
  scale_fill_manual(name = "Organization Type",
                    values = c("Government" = "chocolate2", 
                               "IGO" = "steelblue", 
                               "Think Tank" = "darkolivegreen3", 
                               "NGO" = "steelblue1", 
                               "University" = "gray30",
                               "Legislative Body" = "chocolate4")) +
  labs(caption = "Data source: Overton.io") +
  theme(legend.position = "bottom")
```

Analysis of policy documents that cite my research identifies the main topics where my work has been influential. In Fig. \ref{fig:policy-impact-topics} we can see the wide range of topics, from the economy and transportation, to air pollution and food security. The topics that my research is found more than expected relate to cycling, bus and rapid transit, accessibility, and public transport.

```{r policy-impact-topics-plot, out.width="0.7\\linewidth", fig.cap="\\label{fig:policy-impact-topics}Policy topics informed by my research"}

policy_impact_topics |> 
  arrange(desc(Document_count)) |>
  slice_head(n = 30) |>
  ggplot(aes(area = Document_count, 
           fill = Reason_highlighted,
           subgroup = Reason_highlighted,
           label = Topic)) +
  geom_treemap() +
  geom_treemap_subgroup_border() +
  geom_treemap_subgroup_text(place = "centre", grow = T, alpha = 0.25, 
                             colour =
                             "black", fontface = "italic", min.size = 0) +
  geom_treemap_text(colour = "white", place = "topleft", reflow = T) +
  scale_fill_manual(name = "Frequency of topic",
                    values = c("seen frequently" = "steelblue", 
                               "seen more often than expected in this context" = "darkolivegreen3")) +
  labs(caption = "Data source: Overton.io") +
  theme(legend.position = "bottom")
```

# Research Output

It is conventional in my fields of expertise to list authors in order of their contributions. The first and second authors are credited with doing a majority of the work. The exception to this general rule is when the last author is the senior author and has provided, in addition to other contributions, supervisory support to the rest of the team.

## At a Glance

Table \ref{tab:bibliography-at-a-glance} provides some key information about my publication record. In addition to the items listed there, I am co-editor of `r bibliography_entries(paste0(here(),"/assets/edited-books.bib")) |> nrow()` edited books. Fig. \ref{fig:key-topics} maps the relationship between key topics in my peer-reviewed publications, based on keywords of the documents. Fig. \ref{fig:intl-colabs} maps my international research collaborations.

```{r}
kable(bibliography_glance,
      "latex",
      col.names = c("Type", 
                    "No. of Items",
                    "Mean No. Authors",
                    "Max. No. Authors", 
                    "Single Author", 
                    "First Author", 
                    "Second Author", 
                    "Senior Author", 
                    "Other Author"),
      booktabes = TRUE,
      caption = "\\label{tab:bibliography-at-a-glance}Bibliography at a glance") |>
  kable_styling(font_size = 7, 
                latex_options = "HOLD_position")
```

```{r convert-bibliography-for-bibliometric-analysis, include=FALSE}
# This chunk uses package {bibliometrix}

M <- convert2df(glue::glue(here::here(), "/assets/wos_0.bib"),
                dbsource = "wos",
                format = "bibtex")
```

```{r key-word-co-occurrences, include=FALSE}
# This chunk uses package {bibliometrix}

NetMatrix <- biblioNetwork(M, 
                           analysis = "co-occurrences", 
                           network = "keywords", 
                           sep = ";")

net <- networkPlot(NetMatrix, 
                   normalize="association", 
                   weighted = T, 
                   n = 35, 
                   Title = "Keyword Co-occurrences", 
                   type = "fruchterman", 
                   size = TRUE,
                   edgesize = 5,
                   labelsize=0.5)

graph <- as_tbl_graph(net$graph)
```

```{r key-research-themes}
set.seed(35)

key_research_themes <- ggraph(graph |>
                                filter(!str_detect(name, "hamilton")) |>
                                mutate(name = str_to_title(name)),
                              layout = "fr") +
  geom_edge_fan(aes(alpha = weight)) +
  geom_node_label(aes(color = factor(community),
                      label = name,
                      size = size),
                  repel = TRUE) +
  scale_size_continuous(range = c(2.5, 4.5)) +
  theme_void() +
  theme(legend.position = "none")
```

```{r network-of-collaborations, include=FALSE}
# This chunk uses package {bibliometrix}

M <- metaTagExtraction(M, Field = "AU_CO", sep = ";")

NetMatrix <- biblioNetwork(M, 
                           analysis = "collaboration", 
                           network = "countries", sep = ";")

net <- networkPlot(NetMatrix, 
                   n = dim(NetMatrix)[1], 
                   label.cex = TRUE,
                   Title = "Country Collaboration", 
                   type = "circle", size=TRUE, 
                   remove.multiple=FALSE,
                   labelsize=0.7,
                   cluster="none")

graph <- as_tbl_graph(net$graph)
```

```{r plot-network-of-collaborations}
intl_collabs <- ggraph(graph  |>
                         mutate(name = str_to_title(name),
                                name = ifelse(name == "Usa", "USA", name)), 
                       layout = "linear", 
                       circular = TRUE) +
  geom_edge_fan(aes(alpha = weight)) +
  geom_node_label(aes(label = name,
                      size = size)) +
  scale_size_continuous(range = c(2.5, 4.5)) +
  theme_void() +
  theme(legend.position = "none")
```

```{r key-topics-plot, out.width="0.7\\linewidth", fig.cap="\\label{fig:key-topics}Key topics in my peer-reviewed publications"}
key_research_themes
```

```{r intl-colabs-plot, out.width="0.6\\linewidth", fig.cap="\\label{fig:intl-colabs}International collaborations"}
intl_collabs
```

\newpage

# Lifetime Publications

## Books

```{r books}
bibliography_entries(paste0(here(),"/assets/books.bib")) |>
  arrange(desc(issued), desc(author$family))
```

## Edited Books

```{r edited-books}
bibliography_entries(paste0(here(),"/assets/edited-books.bib")) |>
  #bibliography_entries(paste0(here(),"/assets/savedrecs_2.bib")) |>
  arrange(desc(issued), desc(author$family))
```

## Book Chapters

```{r book-chapters}
bibliography_entries(paste0(here(),"/assets/book-chapters.bib")) |>
  #bibliography_entries(paste0(here(),"/assets/savedrecs_2.bib")) |>
  arrange(desc(issued), desc(author$family))
```


## Reports 

```{r reports}
bibliography_entries(paste0(here(),"/assets/reports.bib")) |>
  #bibliography_entries(paste0(here(),"/assets/savedrecs_2.bib")) |>
  arrange(desc(issued), desc(author$family))
```

<!--
\newpage
-->

## Peer-Reviewed Journal Articles (Published)

```{r journal-articles-published}
bibliography_entries(paste0(here(),"/assets/refereed-publications.bib")) |>
  arrange(desc(issued), desc(author$family))
```

## Peer-Reviewed Journal Articles (Accepted for Publication in Final Form)

```{r journal-articles-accepted-for-publication, results='asis'}
rpa <- bibliography_entries(paste0(here(),"/assets/refereed-publications-accepted.bib"))

# Check that the table is not empty
if(nrow(rpa) > 0){
  rpa |>
    arrange(desc(issued), desc(author$family))
}
```

<!--
\newpage
-->

## Peer-Reviewed Journal Articles (Submitted for Publication)

```{r journal-articles-submitted-for-publication}
rsp <- bibliography_entries(paste0(here(),"/assets/refereed-publications-submitted.bib")) 

# Check that the table is not empty
if(nrow(rsp) > 0){
  rsp |>
    arrange(desc(issued), desc(author$family))
}
```

<!--
\newpage
-->

## Work in Progress

```{r work-in-progress}
bibliography_entries(paste0(here(),"/assets/work-in-progress.bib")) |>
  arrange(desc(issued), desc(author$family))
```



## Peer-reviewed Conference Presentations

```{r peer-reviewed-conference-presentations}
peer_reviewed_conference <- bibliography_entries(paste0(here(),"/assets/conference-presentations-peer-reviewed.bib")) |>
  arrange(desc(issued), desc(author$family))

peer_reviewed_conference
```

<!--Number of lifetime peer-reviewed conference presentations is `r nrow(peer_reviewed_conference)`.-->

## Non-peer-reviewed Conference Presentations

```{r not-peer-reviewed-conference-presentations, include=FALSE}
non_peer_reviewed_conference <- bibliography_entries(paste0(here(),"/assets/conference-presentations-not-peer-reviewed.bib")) |>
  arrange(desc(issued), desc(author$family))
```

Number of lifetime non-peer-reviewed conference presentations is `r nrow(non_peer_reviewed_conference)`.

# Knowledge Mobilization Activities

```{r unsolicited-advice-details}
read_csv(paste0(here(),"/assets/talks.csv")) |>
  filter(What == "Workshop" ) |>
  detailed_entries(what = Organization, 
                   when = Year, 
                   with = Title,
                   where = Where,
                   why = paste0(What, ", ", Role),
                   .protect = FALSE)
```

# Invited Talks, Seminars, and Panels

```{r talks-courses-details}
talks <- read_csv(paste0(here(),"/assets/talks.csv")) |>
  filter(What != "Workshop") |>
  detailed_entries(what = Organization, 
                   when = Year, 
                   with = Title,
                   where = Where,
                   why = paste0(What, ", ", Role),
                   .protect = FALSE)
```

## Lifetime Talks, Seminars, and Panels

My lifetime number of talks is `r nrow(talks)`.

## Details

```{r}
talks
```

# External Service

```{r external-service-details}
read_csv(paste0(here(),"/assets/service-external.csv")) |>
  arrange(desc(Start)) |>
  detailed_entries(what = Where, 
                   when = case_when(Start != End ~ glue::glue("{Start}-{End}"),
                                    Start == End ~ as.character(Start)),
                   with = Organization,
                   where = Position,
                   .protect = FALSE)
```

# Internal (Departmental, Faculty, University) Service (Most Recent 10 Years)

```{r internal-service-details}
read_csv(paste0(here(),"/assets/service-internal.csv")) |>
  detailed_entries(what = Where, 
                   when = Year, 
                   with = Organization,
                   where = Position)
```

