---
name: Antonio
surname: Paez
position: "Professor"
address: |
         | School of Earth, Environment and Society
         | McMaster University
         | 1280 Main St West, Hamilton, Ontario, Canada L8S 1S4
phone: +1 905 525 9140
www: experts.mcmaster.ca/display/paezha
email: "paezha@mcmaster.ca"
orcid: 0000-0001-6912-9919
github: paezha
publons: 2897251
#researchgate: 7004827878
googlescholar: paezha
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    page_total: true
    extra_dependencies: ["flafter"]
---

```{r knitr-setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE,
                      fig.show='asis', 
                      out.width="0.6\\linewidth", 
                      fig.align='center')
```

```{r current-year}
# Retrieve current year
current_year <- as.numeric(as.character(Sys.time(), '%Y')) # Update year
```

```{r load-packages}
library(here)
library(readr)
library(scholar)
library(tibble)
library(tidyverse)
library(vitae)
```

# About me

 * I trained in civil engineering before being adopted into geography.
 * My areas of interest include spatial analysis, spatial statistics, transportation, travel behavior, cities.
 * Also, too, mathematics, computer languages, science fiction, poetry, and memes.
 * I have been known to look professorial on occasion.
 * At this rate my only hope of being recognized is as the most promising oldest researcher in my discipline.

# Education

```{r education-details}
read_csv(paste0(here(),"/assets/education.csv")) %>% 
  detailed_entries(what = Degree, 
                   when = Year, 
                   with = Institution,
                   where = Where, 
                   why = Thesis,
                   .protect = FALSE)
```

# Current Status at McMaster

Full Professor in the School of Earth, Environment and Society since 2014. Tenured since 2007.

# Employment History

## Academic

```{r employment-details}
read_csv(paste0(here(),"/assets/employment.csv")) %>% 
  detailed_entries(what = Position, 
                   when = Year, 
                   with = Organization,
                   where = Where,
                   .protect = FALSE)
```
# Editorial Activities

```{r editor-details}
read_csv(paste0(here(),"/assets/editorial-board.csv")) |>
  filter(What == "Editor-in-Chief") |>
  detailed_entries(what = Journal, 
                   where = Year,
                   with = What,
                   .protect = FALSE)
```

```{r associate-editor-details}
read_csv(paste0(here(),"/assets/editorial-board.csv")) |>
  filter(What == "Associate Editor") |>
  detailed_entries(what = Journal, 
                   where = Year,
                   with = What,
                   .protect = FALSE)
```

```{r editorial-board-details}
read_csv(paste0(here(),"/assets/editorial-board.csv")) |>
  filter(What == "Editorial Board Member") |>
  detailed_entries(what = Journal, 
                   where = Year,
                   with = What,
                   .protect = FALSE)
```

# Scholarly and Professional Activities

## Journal Referee

```{r journal-referee}
referee <- read_csv(paste0(here(),"/assets/paper-reviews.csv")) %>% 
  pivot_longer(-Journal, 
               names_to = "Year", 
               values_to = "Reviews")
```

### Number of Total Lifetime Reviews

`r sum(referee$Reviews)`

### Number of Reviews in `r current_year`

`r referee %>% filter(Year == current_year) %>% pull(Reviews) %>% sum()`

# Areas of Interest

Spatial data analysis and statistics; transportation modeling; travel behavior; health geography; Geographic Information Systems.

# Research Impact

Fig. \ref{fig:citations} is a summary of research impact according to Google Scholar.

```{r citations-plot, fig.cap="\\label{fig:citations}Citations per year according to Google Scholar"}
id <- "bLY377kAAAAJ" # Replace with your own google scholar id
citations_scholar <- scholar::get_citation_history(id)

citations_scholar %>%
  ggplot() + 
  geom_col(aes(x = year, 
               y = cites),
           color = "black",
           fill = "white") + 
  annotate(geom = "text", 
           x = 2004, 
           y = 950, 
           hjust = 0,
           label = paste0("Total cites = ", 
                          prettyNum(get_profile(id)$total_cites, big.mark = ","))) +
  annotate(geom = "text", 
           x = 2004, 
           y = 900, 
           hjust = 0,
           label = paste0("h-index = ", 
                          as.character(get_profile(id)$h_index))) +
  annotate(geom = "text", 
           x = 2004, 
           y = 850, 
           hjust = 0,
           label = paste0("i10-index = ", 
                          as.character(get_profile(id)$i10_index))) +
  ggthemes::theme_tufte()
```

# Lifetime Publications

### Edited Books

```{r edited-books}
bibliography_entries(paste0(here(),"/assets/edited-books.bib")) %>%
#bibliography_entries(paste0(here(),"/assets/savedrecs_2.bib")) %>%
  arrange(desc(issued), desc(author$family))
```

### Journal Articles (30 most recent)

```{r journal-articles-published}
bibliography_entries(paste0(here(),"/assets/refereed-publications.bib")) |>
  arrange(desc(issued), desc(author$family)) |>
  slice_head(n = 30)
```

\newpage

# Invited Talks, Seminars, Workshops, Courses, and Panels (15 most recent)

```{r talks-courses-details}
read_csv(paste0(here(),"/assets/talks.csv")) |>
  filter(What != "Unsolicited Advice") |>
  slice_head(n = 15) |>
  detailed_entries(what = Organization, 
                   when = Year, 
                   with = Title,
                   where = Where,
                   why = paste0(What, ", ", Role),
                   .protect = FALSE)
```

