---
name: Antonio
surname: Páez
position: "Professor"
address: |
         | School of Earth, Environment and Society
         | McMaster University
         | 1280 Main St West, Hamilton, Ontario, Canada L8S 1S4
phone: +1 905 525 9140
www: experts.mcmaster.ca/display/paezha
email: "paezha@mcmaster.ca"
orcid: 0000-0001-6912-9919
github: paezha
publons: 2897251
#researchgate: 7004827878
googlescholar: paezha
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    page_total: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE)
library(here)
library(readr)
library(scholar)
library(tibble)
library(tidyverse)
library(vitae)
```

# About me

 * I trained in civil engineering before being adopted into geography.
 * My areas of interest are spatial analysis, spatial statistics, transportation, travel behavior, cities.
 * At this rate my only hope of being recognized is as most promising oldest researcher in my discipline.

# Education

```{r education-details}
read_csv(paste0(here(),"/assets/education.csv")) %>% 
  detailed_entries(what = Degree, 
                   when = Year, 
                   with = Institution,
                   where = Where, 
                   why = Thesis,
                   .protect = FALSE)
```

# Current Status at McMaster

Full Professor in the School of Earth, Environment and Society since 2014. Tenured since 2007.

# Employment History

## Academic

```{r employment-details}
read_csv(paste0(here(),"/assets/employment.csv")) %>% 
  detailed_entries(what = Position, 
                   when = Year, 
                   with = Organization,
                   where = Where,
                   .protect = FALSE)
```

# Industry

Surveyor and construction site supervisor (August 1993 – March 1995) Topographical
survey projects in Nuevo León, Mexico, sponsored by various Municipal Public Works Departments (Monterrey, Guadalupe, Santa Catarina), and by Mercedes-Benz. These projects involved in-field data collection and computer aided design. Construction site supervision.

# Areas of Interest

Spatial data analysis and statistics; transportation modeling; travel behavior; health geography; Geographic Information Systems.

# Honours

## Visiting Professorships

```{r professorship-details}
read_csv(paste0(here(),"/assets/honors.csv")) %>%
  dplyr::filter(Type == "Professorship") %>% 
  detailed_entries(what = Honor, 
                   when = Year, 
                   with = Organization,
                   where = Where,
                   .protect = FALSE)
```

## Scholarships

```{r scholarships-details}
read_csv(paste0(here(),"/assets/honors.csv")) %>%
  dplyr::filter(Type == "Scholarship") %>% 
  detailed_entries(what = Honor, 
                   when = Year, 
                   with = Organization,
                   where = Where,
                   .protect = FALSE)
```

## Scientific Awards

```{r scientific-awards-details}
read_csv(paste0(here(),"/assets/honors.csv")) %>%
  dplyr::filter(Type == "Scientific Awards") %>% 
  detailed_entries(what = Honor, 
                   when = Year, 
                   with = Organization,
                   where = Where,
                   why = With,
                   .protect = FALSE)
```

## Trainee Honours

```{r trainee-honors-details}
read_csv(paste0(here(),"/assets/honors.csv")) %>%
  dplyr::filter(Type == "Trainee") %>% 
  detailed_entries(what = Organization, 
                   when = Year, 
                   with = With,
                   where = Honor,
                   .protect = FALSE)
```

# Supervisorships

## Undergraduate

## Diploma and Certificate

## Master

## Ph.D.

# Supervisory Committees

# Examination Committees

# Research and Other Funding

# Research Impact

Fig. \ref{fig:citations} is a summary of research impact according to Google Scholar.

```{r citations-plot, fig.show='asis', out.width="0.7\\linewidth", fig.align='center', fig.cap="\\label{fig:citations}Citations per year according to Google Scholar"}
id <- "bLY377kAAAAJ"
citations_scholar <- scholar::get_citation_history(id)

citations_scholar %>%
  ggplot() + geom_col(aes(x = year, 
                          y = cites)) + 
  annotate(geom = "text", 
           x = 2004, 
           y = 950, 
           hjust = 0,
           label = paste0("Total cites = ", 
                          prettyNum(get_profile(id)$total_cites, big.mark = ","))) +
  annotate(geom = "text", 
           x = 2004, 
           y = 900, 
           hjust = 0,
           label = paste0("h-index = ", 
                          as.character(get_profile(id)$h_index))) +
  annotate(geom = "text", 
           x = 2004, 
           y = 850, 
           hjust = 0,
           label = paste0("i10-index = ", 
                          as.character(get_profile(id)$i10_index))) +
  ggthemes::theme_tufte()
```

# Lifetime Publications

## Peer-Reviewed 

### Edited Books

### Book Chapters

### Journal Articles

```{r}
bibliography_entries(paste0(here(),"/assets/refereed-publications.bib")) %>%
#bibliography_entries(paste0(here(),"/assets/savedrecs_2.bib")) %>%
  arrange(desc(issued), desc(author$family))
```

### Conference Presentations and Proceedings

## Accepted for Publication in Final Form

```{r}
bibliography_entries(paste0(here(),"/assets/accepted-for-publication.bib")) %>%
#bibliography_entries(paste0(here(),"/assets/savedrecs_2.bib")) %>%
  arrange(desc(issued), desc(author$family))
```

## Submitted for Publication

```{r}
bibliography_entries(paste0(here(),"/assets/submitted-for-publication.bib")) %>%
#bibliography_entries(paste0(here(),"/assets/savedrecs_2.bib")) %>%
  arrange(desc(issued), desc(author$family))
```

# Invited Talks, Seminars and Courses

```{r talks-courses-details}
read_csv(paste0(here(),"/assets/talks.csv")) %>%
  #dplyr::filter(Type == "Trainee") %>% 
  detailed_entries(what = What, 
                   when = Year, 
                   with = Role,
                   where = Where,
                   .protect = FALSE)
```