---
name: Antonio
surname: Paez
position: "Professor"
address: |
         | School of Earth, Environment and Society
         | McMaster University
         | 1280 Main St West, Hamilton, Ontario, Canada L8S 1S4
phone: +1 905 525 9140
www: experts.mcmaster.ca/display/paezha
email: "paezha@mcmaster.ca"
orcid: 0000-0001-6912-9919
github: paezha
publons: 2897251
#researchgate: 7004827878
googlescholar: paezha
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    page_total: true
    extra_dependencies: ["flafter"]
header-includes:
  - \usepackage{soul}
---

```{r knitr-setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE,
                      fig.show='asis', 
                      out.width="0.6\\linewidth", 
                      fig.align='center')

#pandoc::pandoc_activate()
```

```{r load-packages}
library(dplyr) # A Grammar of Data Manipulation
library(ggplot2) # Create Elegant Data Visualisations Using the Grammar of Graphics
library(glue) # Interpreted String Literals
library(here) # A Simpler Way to Find Your Files
library(lubridate) # Make Dealing with Dates a Little Easier
library(readr) # Read Rectangular Text Data
library(scholar) # Analyse Citation Data from Google Scholar
library(tibble) # Simple Data Frames
library(tidyr) # Tidy Messy Data
library(vitae) # Curriculum Vitae for R Markdown
```

```{r current-year}
# Retrieve current year
current_year <- lubridate::year(Sys.time()) # Update year
```

# About me

 * I trained in civil engineering before being adopted into geography.
 * My areas of interest include spatial analysis, spatial statistics, transportation, travel behavior, cities.
 * Also, too, mathematics, computer languages, science fiction, poetry, and memes.
 * I have been known to look professorial on occasion.
 * In 2010 a research team I led was recognized with the **Meredith F. Burrill  Award** of the Association of American Geographers for exceptional work at the intersection basic research in geography and policy.
 * In 2024 I was recognized with the **Edward L. Ullman Award** of the Association of American Geographers for lifelong commitment and contributions to the field of transportation geography.

# Education

```{r education-details}
read_csv(paste0(here(),"/assets/education.csv")) |> 
  detailed_entries(what = Degree, 
                   when = Year, 
                   with = Institution,
                   where = Where, 
                   why = Thesis,
                   .protect = FALSE)
```

# Current Status at McMaster

Full Professor in the School of Earth, Environment and Society since 2014. Tenured since 2007.

# Employment History

## Academic

```{r employment-details}
read_csv(paste0(here(),"/assets/employment.csv")) |> 
  detailed_entries(what = Position, 
                   when = Year, 
                   with = Organization,
                   where = Where,
                   .protect = FALSE)
```

## Industry

Surveyor and construction site supervisor (August 1993 - March 1995) Topographical
survey projects in Nuevo León, Mexico, sponsored by various Municipal Public Works Departments (Monterrey, Guadalupe, Santa Catarina), and by Mercedes-Benz. These projects involved in-field data collection and computer aided design. Construction site supervision.

\newpage

# Editorial Activities

```{r editor-details}
read_csv(paste0(here(),"/assets/editorial-board.csv")) |>
  filter(What == "Editor-in-Chief") |>
  detailed_entries(what = Journal, 
                   where = Year,
                   with = What,
                   .protect = FALSE)
```

```{r associate-editor-details}
read_csv(paste0(here(),"/assets/editorial-board.csv")) |>
  filter(What == "Associate Editor") |>
  detailed_entries(what = Journal, 
                   where = Year,
                   with = What,
                   .protect = FALSE)
```

```{r guest-editor-details}
read_csv(paste0(here(),"/assets/editorial-board.csv")) |>
  filter(What == "Guest Editor") |>
  detailed_entries(what = Editors, 
                   when = Year,
                   with = What,
                   where = glue::glue("{Journal} {Volume}"),
                   why = Title,
                   .protect = FALSE)
```

```{r editorial-board-details}
read_csv(paste0(here(),"/assets/editorial-board.csv")) |>
  filter(What == "Editorial Board Member") |>
  detailed_entries(what = Journal, 
                   where = Year,
                   with = What,
                   .protect = FALSE)
```

# Scholarly and Professional Activities

## Journal Referee

```{r journal-referee}
referee <- read_csv(paste0(here(),"/assets/paper-reviews.csv")) |> 
  pivot_longer(-Journal, 
               names_to = "Year", 
               values_to = "Reviews")
```

### Number of Total Lifetime Reviews

`r sum(referee$Reviews)`

### Number of Reviews in `r current_year`

`r referee |> filter(Year == current_year) |> pull(Reviews) |> sum()`

### Reviews-to-Publications per Year

Fig. \ref{fig:reviews-pubs} is a summary of journal reviews-to-publications per year showing contributions to peer-review relative to demands on peer-review.

```{r reviews-per-year, include=FALSE, fig.cap="\\label{fig:reviews-annual-summary}Number of journal reviews per year"}
referee |>
  group_by(Year) |>
  summarize(Reviews = sum(Reviews),
            .groups = "drop") |>
  ggplot() +
  geom_col(aes(x = Year, y = Reviews)) +
  ggthemes::theme_tufte() +
  theme(axis.text = element_text(angle = 45))
```

```{r review-to-publication, fig.cap="\\label{fig:reviews-pubs}Reviews-to-publications by year"}
# Check publication vs. review activity
df_pubs <- bibliography_entries(paste0(here(),"/assets/refereed-publications.bib"))
df_pubs <- data.frame(Year = df_pubs$issued |> 
                        unlist()) |>
  group_by(Year) |>
  summarize(items = n(),
            .groups = "drop") |>
  mutate(type = "Publication")

df_referee <- referee |>
  group_by(Year) |>
  summarize(items = sum(Reviews),
            .groups = "drop") |>
  mutate(type = "Paper Review")

rbind(df_pubs,
      df_referee) |>
  ggplot() +
  geom_col(aes(x = Year,
               y = items,
               fill = type),
           color = "black",
           position = position_dodge(preserve = "single")) +
  scale_fill_manual(values = c("Publication" = "white", "Paper Review" = "black")) +
  ggthemes::theme_tufte() +
  theme(axis.text.x = element_text(angle = 45),
        legend.title = element_blank())
```

### Reviews per journal

```{r journal-referee-details}
referee |>
  group_by(Journal) |> 
  summarize(Reviews = sum(Reviews), 
            .groups = "drop") |>
  detailed_entries(what = Journal, 
                   when = Reviews,
                   .protect = FALSE)
```

# Grant Reviews

```{r}
read_csv(paste0(here(),"/assets/grant-reviews.csv")) |> 
  arrange(desc(Year)) |>
  detailed_entries(what = Role, 
                   when = glue::glue("Number of reviews: {Number}"), 
                   with = glue::glue("{Funder} ({Where})"),
                   where = Year,
                   .protect = FALSE)
```



# Areas of Interest

Spatial data analysis and statistics; transportation modeling; travel behavior; health geography; Geographic Information Systems.

# Honours

## Visiting Professorships

```{r professorship-details}
read_csv(paste0(here(),"/assets/honors.csv")) |>
  dplyr::filter(Type == "Professorship") |> 
  detailed_entries(what = Honor, 
                   when = Year, 
                   with = Organization,
                   where = Where,
                   .protect = FALSE)
```

## Scholarships

```{r scholarships-details}
read_csv(paste0(here(),"/assets/honors.csv")) |>
  dplyr::filter(Type == "Scholarship") |> 
  detailed_entries(what = Honor, 
                   when = Year, 
                   with = Organization,
                   where = Where,
                   .protect = FALSE)
```

## Scientific Awards

```{r scientific-awards-details}
read_csv(paste0(here(),"/assets/honors.csv")) |>
  dplyr::filter(Type == "Scientific Awards") |> 
  detailed_entries(what = Honor, 
                   when = Year, 
                   with = Organization,
                   where = Where,
                   why = With,
                   .protect = FALSE)
```

## Trainee Honours

```{r trainee-honors-details}
read_csv(paste0(here(),"/assets/honors.csv")) |>
  dplyr::filter(Type == "Trainee") |> 
  detailed_entries(what = Organization, 
                   when = Year, 
                   with = With,
                   where = Honor,
                   .protect = FALSE)
```

## Other

```{r other-honors-details}
read_csv(paste0(here(),"/assets/honors.csv")) |>
  dplyr::filter(Type == "Other") |> 
  mutate(Year = current_year) |>
  detailed_entries(what = Organization, 
                   when = Year, 
                   with = Honor,
                   why = With,
                   .protect = FALSE) |>
  mutate(Year = current_year)
```

# Teaching

<!--
## Courses

```{r courses, eval=FALSE}
courses <- read_csv(paste0(here(),"/assets/courses-taught.csv")) 

courses |>
  detailed_entries(what = Level, 
                   when = glue::glue("TA support (1 TA = 130 h): {Tas}/ Co-Instructor(s): {Coinstructor}"),
                   where = glue::glue("{Year} ({Session})"),
                   with = glue::glue("{Code} {Name}"),# glue("{Code}, {Name}"),
                   why = glue::glue("Enrolment: {Enrolment} students"),
                   .protect = FALSE)
```
-->

<!-- Compressed version of courses -->

## Undergraduate Teaching

```{r courses-brief-undergraduate}
courses <- read_csv(paste0(here(),"/assets/courses-taught.csv")) 

courses_summary <- courses |>
  group_by(Code) |> 
  summarize(Name = first(Name), 
            offerings = n(),
            total_students = sum(Enrolment), 
            level = first(Level)) |> 
  arrange(level)

courses_summary |>
  filter(level == "Undergraduate") |>
  detailed_entries(what = glue::glue("Total enrolment: {total_students} students"), 
                   when = Name,
                   where = glue::glue("Times offered: {offerings}"),
                   with = Name,
                   .protect = FALSE)
```

## Graduate Teaching

```{r courses-brief-graduate}
courses_summary |>
  filter(level == "Graduate") |>
  detailed_entries(what = glue::glue("Total enrolment: {total_students} students"), 
                   when = Name,
                   where = glue::glue("Times offered: {offerings}"),
                   with = Name,
                   .protect = FALSE)
```

## Diploma-Certificate Teaching

```{r courses-brief-diploma}
courses_summary |>
  filter(level == "Diploma-Certificate") |>
  detailed_entries(what = glue::glue("Total enrolment: {total_students} students"), 
                   when = Name,
                   where = glue::glue("Times offered: {offerings}"),
                   with = Name,
                   .protect = FALSE)
```

## Total number of courses taught

`r paste0("Undergraduate: ", courses |> filter(Level == "Undergraduate") |> nrow())`

`r paste0("Graduate: ", courses |> filter(Level == "Graduate") |> nrow())`

## Total number of students

`r paste0("Undergraduate: ", courses |> filter(Level == "Undergraduate") |> pull(Enrolment) |> sum())`

`r paste0("Graduate: ", courses |> filter(Level == "Graduate") |> pull(Enrolment) |> sum())`

# Supervisorships

## Undergraduate (Civil Engineering):

Zibby Petch (McMaster University, April 2010) Short term bike facility utilization study (undergraduate project)

Karolina Krol (McMaster University, April 2009) Urban form and transportation patterns, data collection and organization

## McMaster Engineering and Society Program - Metrolinx Rob MacIsaac Fellowship:
Josh Arbess (McMaster University, January 2020 – June 2020) Mapping the Adoption of Mobility-as-a-Service in the Greater Toronto and Hamilton Area: An Analysis of Demographics, Travel Patterns and Technology (with Sanathan Kassiedass, Senior Advisor,  Innovation and New Mobility – Metrolinx)

## McMaster Engineering and Society Program - Inquiry Paper:

Josh Arbess (McMaster University, April 2021) The 15-minute neighborhood

Samuel Greg Smilski (McMaster University, April 2020) What factors influence the supply and demand of affordable housing in Hamilton, and how can the development of the LRT contribute to alleviating the affordable housing crisis?

Gabriela Tokarska (McMaster University, April 2013) Transit system integration in the Greater Toronto and Hamilton Area

Mike McKnight (McMaster University, April 2012) Why are there so few high-occupancy vehicles in the road today?

Alexander Eryuzlu (McMaster University, April 2009) An Inquiry into the Sustainability of Waste-to-Energy Conversion Facilities: An Analysis of the Environmental, Social, and Economic Perspectives

Adam Howell (McMaster University, April 2008) Mobility tools ownership in Hamilton: Analysis and implications

Doug C. Sharpe (McMaster University, April 2006) Urban form and sustainable transport in Hamilton

Justin M. Potalivo (McMaster University, April 2005) Electronic Devices and Traffic Control and Mitigation Strategies: What is their Role in the City of Hamilton?

Matt G. Sonnenberg (McMaster University, April 2005) Futures and Issues in Public Transportation in the Greater Toronto Area

## Undergraduate (Geography):

Subaita Refaaf (McMaster University, April 2021) Methods of Increasing Ontario's Transit System Efficiency and Ridership via Technological Innovations 
William Li (McMaster University, August 2019) Comparing Tokyo and Vancouver: Transportation Planning for Urban Railways

Dylan Ward (McMaster University, April 2019) Retrofitting Suburban Transit

Ruikang Lin (McMaster University, December 2018) How can light rail transits (LRTs) contribute to improvement of cities? Case studies around the world using a Socio-Ecological Model (SEM)

Alexander Moriopoulous (McMaster University, December 2018) Walkability

Tyler Marr (McMaster University, April 2018) Tactical Urbanism

Jill Scott (McMaster University, Summer 2017) Night Walkability of Hamilton, Ontario As Viewed by the City's Deaf Community (Undergraduate Research Summer Award)

Bingjie Zhu (McMaster University, Summer 2017) Comparing renewable energy development between Germany and Canada (Independent Study in Earth and Environmental Science)

Emily Byford (McMaster University, April 2017) Transportation and Personal Well-Being: How Active and Passive Travel Impact Environmental, Physical and Mental Well-Being of Transportation Users (Independent Study in Geography)

Katelyn Penney (McMaster University, Terms 1-2, 2014-2015) Parks and BMI

Katelyn Penney (McMaster University, April 2013) Traffic Predictions of the Potential Removal of The Gardiner Expressway

Christine Fandrich (McMaster University, April 2012) Estimating McMaster's Transportation Carbon Footprint

David Snell (McMaster University, April 2009) A qualitative analysis of access to public transportation in Toronto, Ontario

Steve Gitao (McMaster University, April 2005) A Spatial Analysis of University Donations: The Case of McMaster University (with Pavlos Kanaroglou)

## Undergraduate (Life Sciences):

Nadhiyya Shabir (McMaster University, April 2021) The Occurrences of Infectious Outbreaks in Toronto Long-Term Healthcare Facilities: 2016-2020

## Undergraduate (Physics):

Salvatore Vivona (McMaster University, April 2017) Using Blended Two-Stage Floating Catchment Areas to Calculate Accessibility to Primary Health Care by Seniors


## Master

Mahdis Moghadasi (McMaster University; September 2021-in progress) Developing data-driven standards for evaluation of active transportation equity

Niloofar Nalaee (McMaster University, September 2021 - in progress) Mobility analytics using social media

Bruno Dias dos Santos (INPE, Brazil, May 2023) Identifying urban and socio-environmental patterns of Amazon cities (with Silvana Amaral and Carolina Pinho)

John Merral (McMaster University, September 2021) School closures and property values in Hamilton

Elise Desjardins (McMaster University; Masters in Public Health, September 2020) Cycling patterns in Hamilton

Sean Sears (McMaster University, July 2020) Goods movement in Canada

Zoha Anjum (McMaster University; Masters in Public Health, September 2019) Water and health in Kenya (co-supervised with Sarah Dickson and Corinne Wallace) 

Rodrigo Victoriano (Universidad de Concepcion, Chile; January 2018) Time, Space, Money, and Social Interaction: Using Machine Learning to Classify People's Mobility Strategies through Four Key Dimensions (with Juan A. Carrasco)

Alvaro E. Toledo (Universidad de Concepcion, Chile; January 2018) A Spatial Analysis of the Impacts of a New Subway Line on Public Transport Demand Using Smart Card Data (with Juan A. Carrasco)

Christine Fandrich (McMaster University; September 2017 - withdrew from program) Housing prices in Hamilton

Edivaldo C. Neves (Universidade Federal de Pernambuco, August 2013) Poles of Crime in Recife: A Spatial Analysis (with Tatiane Menezes).

Mario Reyes (McMaster University; September 2013) Cycling infrastructure, data collection and analysis.

Sammara C. Soares (Universidade Federal de Pernambuco, August 2012) Inequalities in self-assessed health in Brazil (with Tatiane Menezes).

Kristina Cimaroli (McMaster University; September 2012) Donor return behavior (with K. Bruce Newbold).

Jarin Esita (McMaster University; June 2012) Accessibility to blood donation clinics: an individual approach.

Eduardo Barbosa (Universidad de Sao Paulo, Brazil; December 2011) Climate change and land use patterns in Brazil (with Eduardo Haddad)

Cristian Bustos (Universidad de Concepcion, Chile; December 2011) The geography of social networks in Concepcion, Chile (with Juan A. Carrasco)

Md Moniruzzaram (McMaster University; September 2011) Accessibility and built environment effects on transit use.

Kate Whalen (McMaster University; September 2011) Travel preferences and choices of university students and the role of active travel.

Nicolas M. Cespedes (Universidad de Concepcion, Chile; February 2011) T-communities and spatial autocorrelation (with Juan A. Carrasco).

Adam Drackley (McMaster University; July 2010) Blood donor behavior in Canada: A disaggregate analysis (with K. Bruce Newbold).

P.J. Saberton (McMaster University; July 2010) An investigation into the geographical variations in blood donation in Canada's major population centers (with K. Bruce Newbold).

Ana Maria Bonomi Barufi (Universidad de Sao Paulo, Brazil; February 2010) Infant mortality in Brazil (with Eduardo Haddad)

Ivy Dam (McMaster University; September 2009) Telework and the structure of workplace social interactions (with Darren M. Scott)

Natalia Andrea Ruminot Villegas (Universidad de Concepcion, Chile; August 2009) Vulnerable nodes in networks: An autocorrelation approach (with Juan A. Carrasco)

Felipe Antonio Sanhueza Cardenas (Universidad de Concepcion, Chile; August 2009) Data collection and analysis of mode choice at McMaster University (with Juan A. Carrasco)

Julien Bonin (McMaster University; September 2008) Travel behavior of shoppers in Canada: Urban and rural perspectives

Fei Long (McMaster University; June 2006) Spatial Analysis of Real Estate Data: The Case of the City of Toronto

Kenji Kawai (Tohoku University; April 2002) Interpolation of Spatial Data in Urban Models based on Geographically Weighted Regression and Kriging (with Kazuaki Miyamoto)

Eri Yamada (Tohoku University; March 2001) Accessibility Analysis of Transportation Networks in Eastern Asia (with Kazuaki Miyamoto)

## Doctoral

Bruno Dias dos Santos (INPE, Brazil, May 2023) Identifying urban and socio-environmental patterns of Amazon cities (with Silvana Amaral and Carolina Pinho)

Anastasia Soukhov (McMaster University; September 2021-in progress) Developing data-driven standards for evaluation of motorized transportation equity

Elise Desjardins (McMaster University; September 2020-in progress) Children independent mobility

Fernando Romero (Universidad Politecnica de Madrid; September 2019-September 2020) Acceptability of Traffic Demand Management Measures (with José Manuel Vasallo)

Tatiana Ferrari Kolodin (Universidade Federal de Minas Gerais; September 2019-in progress) Urban Form and Sustainable Transportation (with Pedro Amaral)

Faten Almjlad (McMaster University; September 2017-withdrew from program)

Mario Reyes (McMaster University; 2013-withdrew from program) Cycling travel behavior

Daniel Del Bianco (McMaster University; 2012-in progress) Assessing the Impact of Elementary School Closures in the City of Hamilton

Kate Whalen (McMaster University; 2011-2020) The Role of Reflection in Learning through Experience: A Framework and Guide for Students and Educators.

Li He (McMaster University; September 2016) Methodological considerations on the spatial and temporal analysis of violent crime patterns and the identification of social and environmental correlates of crime

Md Moniruzzaram (McMaster University; June 2014) Mobility in Aging: Travel behavior and Implications for Physical Activity.

Lucia Mejia (Universidad Politecnica de Madrid; April 2011) Transportation Infrastructure Impacts on House Prices and Firms' Location: The Effect of a New Metro Line in the Suburbs of Madrid (with Jose Manuel Vasallo)

Steven Farber (McMaster University; June 2010) The social costs of automobility

Ruben Mercado (McMaster University; August 2007) Policy perspectives on transportation and aging

# Supervisory Committees (All are doctoral unless otherwise noted)

Ricardo Lourenco Barros (McMaster University; 2022-) Understanding vegetation dynamics with satellite observations and Explainable Artificial Intelligence (XAI)

Samira Hamidetehrani (McMaster University; 2020-) User Preferences and Intentions Regarding Shared Automated Vehicles in Canadian Metropolitan Areas 

Christina Borowiec (McMaster University; 2019-) Active travel

Shaila Jamal (McMaster University; 2023) Generational differences in travel behavior 

Jeremy Gabriel (McMaster University; 2023) Strata analysis

Elnaz Abotalebi (McMaster University; 2019) Consumer stated preferences survey for electric cars

Wade Genders (McMaster University; 2018) Deep Reinforcement Learning Adaptive Traffic Signal Control 

Randy Bui (McMaster University; withdrew from program) Understanding Network Robustness and Critical Roadway Links in the Greater Toronto and Hamilton Area under Short-Term Disruption

Nazila Roofigari-Esfahan (McMaster University; 2016) A Framework for Spatio-Temporal Uncertainty-Aware Scheduling and Control of Linear Projects

Arash Olia (McMaster University; 2016) Modelling and Assessment of the Transportation Potential and Impacts of Connected and Automated Vehicles

Chris Higgins (McMaster University; 2015) A Value Planning Framework for Predicting and
Recapturing the Value of Rapid Transit Infrastructure

Matthew Adams (McMaster University; 2015) Advancing the use of mobile monitoring data for air pollution modelling

Scott Bennett (McMaster University; 2015) Safer walking routes to school: applied and methodological geographies of child pedestrian injury

Sarah Dickin (McMaster University; September 2014) Mapping vulnerability to water-related infectious disease: an ecosystem approach 

Ron Dalumpines (McMaster University; July 2014) Route choice analysis in time-geographic perspective

Kathleen Deutsch (University of California Santa Barbara; June 2013) Sense of place and travel behavior

Andrew Clarke (McMaster University; January 2013) Understanding determinants of active travel

Xudong Liu (McMaster University; withdrew from program in 2011) Integrating firmography in urban models

Jia Yang (McMaster University; withdrew from program in 2011) Modeling firm survival

Renilson Rodriguez da Silva (Universidade de Sao Paulo; completed: March 2011) Accessibility and development in the Amazon region (with Danilo Igliori)

Jamie E.L. Spinney (McMaster University; completed: September 2010) Geography, Land Values, and Municipal Taxation: A Spatial Paradigm for the Estimation and Reclamation of Rent

Kelsey MacCormack (McMaster University; completed: July 2010) Delineation of subsurface gravel units beneath the Dundas Valley, Ontario

Theodora Pouliou (McMaster University; completed: September 2009) Individual and Socio-Environmental Determinants of Obesity in Canada

Hejun Kang (McMaster University; completed: August 2008) Intra-households interactions and travel behavior

Dimitris Potoglou (McMaster University; completed: April 2006) Potential demand for alternative fuelled vehicles in the City of Hamilton CMA

# Examination Committees

Samira Hamidetehrani (Ph.D., McMaster University; School of Earth, Environment and Society ) September 15, 2023

Daniel Van Veghel (M.Sc., McMaster University; School of Earth, Environment and Society ) August 28, 2023

Bruno Dias dos Santos (M.Sc., INPE, Brazil) May 18, 2023

Daniela Arias Molinares (Ph.D., Facultad de Geografía e Historia, Universidad Complutense de Madrid) May 10, 2023

Shaila Jamal (Ph.D. McMaster University; School of Earth, Environment and Society) May 9, 2023

Lucy Joseph Chabariko (Ph.D., School of Transportation Sciences, University of Hasselt) December 21, 2020

Darcy Reynard (Ph.D., Department of Earth and Atmospheric Sciences, University of Alberta) December 18, 2020

Jose Carpio-Pinedo (Ph.D., ETS Arquitectura, Universidad Politecnica de Madrid) November 19, 2020

Sami Kurani (M.A., McMaster University; School of Earth, Environment and Society) September 28, 2020

Geun (Jayden) Choi (M.A., McMaster University; School of Earth, Environment and Society) August 25, 2020

Matthew Brown (M.A., McMaster University; School of Earth, Environment and Society) April 3, 2020

Javier Delso (Ph.D., ETSI Montes, Universidad Politecnica de Madrid) February 25, 2020

Shaila Jamal (Ph.D., Comprehensive Examination, School of Geography and Earth Sciences) February 11, 2020

Kyran Cupido (Ph.D., Arizona State University, School of Mathematics and Statistical Sciences) December 6, 2019

Zoha Anjum (MPH, McMaster University, Health Research Methods, Evidence, and Impact) September 2019

Georgios Sarlas (Ph.D., ETH Zurich, Civil, Environmental, and Geomatics Engineering) July 1, 2019

Matthew Quick (Ph.D., University of Waterloo; School of Planning) April 24, 2019

Wade Genders (Ph.D., McMaster University; Civil Engineering) November 22, 2018

Quinn Hachey (M.A., McMaster University; School of Geography and Earth Sciences) December 18, 2017

Wei Lu (M.A., McMaster University; School of Geography and Earth Sciences) September 28, 2017

Charles Burke (Ph.D., McMaster University; School of Geography and Earth Sciences) December 5, 2016

Nazila Roofigari-Esfahan (Ph.D., McMaster University; Civil Engineering) August 8, 2016

Juan Pablo Ospina Zapata (Ph.D., Comprehensive Examination. Universidad Nacional de Colombia – Medellin; Civil Engineering) June 10, 2016

Arash Olia (Ph.D., McMaster University; Civil Engineering) June 8, 2016

Geraldine Fuenmayor (Ph.D., University of Calgary; Civil Engineering) May 19, 2016

Sadia Yawar (M.A., McMaster University; School of Geography and Earth Sciences) April 29, 2016

An Neven (Ph.D., Hasselt University; School of Transportation Sciences) September 7, 2015

Chris Higgins (Ph.D., McMaster University; School of Geography and Earth Sciences) August 28, 2015

Matthew Adams (Ph.D., McMaster University; School of Geography and Earth Sciences) July 31, 2015

Scott Bennett (Ph.D., McMaster University; School of Geography and Earth Sciences) July 3, 2015

Wade Genders (M.A.Sc., McMaster University; Civil Engineering) November 17, 2014

Sarah Dickin (Ph.D., McMaster University; Geography) September 5, 2014

Simon Minelli (M.A.Sc., McMaster University; Civil Engineering) September 3, 2014

Ron Dalumpines (Ph.D., McMaster University; Geography) July 28, 2014

Markus Botte (Ph.D., University of Western Australia; Business) July 4, 2014

Kathleen Deutsch (Ph.D., University of California Santa Barbara; Geography) June 20, 2013

Chris Higgins (Ph.D., Comprehensive Examination. McMaster University; Geography and Earth Sciences) February 14, 2013

Andrew Clarke (Ph.D., McMaster University; Geography and Earth Sciences) September 24, 2012

Adrian Klisz (M.A., McMaster University; Geography and Earth Sciences) July 24, 2012

Sarah Dickin (Ph.D., Comprehensive Examination. McMaster University; Geography and Earth Sciences) October 24, 2011

Jia Yang (M.A., McMaster University; Geography and Earth Sciences) September 12, 2011

Xudong Liu (M.A., McMaster University; Geography and Earth Sciences) September 12, 2011 

Ron Dalumpines (Ph.D., Comprehensive Examination. McMaster University; Geography and Earth Sciences) December 3, 2010 

Jia Yang (Ph.D., Comprehensive Examination. McMaster University; Geography and Earth Sciences) December 2, 2010

Xudong Liu (Ph.D., Comprehensive Examination. McMaster University; Geography and Earth Sciences) December 2, 2010 

Jamie E.L. Spinney (Ph.D., McMaster University; Geography and Earth Sciences) September 24, 2010

Kelsey McCormack (Ph.D., McMaster University; Geography and Earth Sciences) July 27, 2010

PJ Saberton (M.A., McMaster University; Geography and Earth Sciences) July 26, 2010

Adam Drackley (M.A., McMaster University; Geography and Earth Sciences) July 26, 2010

Kathleen Deutsch (Ph.D., Proposal Defense. University of California Santa Barbara) April 14, 2010

Daniela Schettini (Ph.D., Universidade de São Paulo; Economics) April 9, 2010

Ana Maria Bonomi Barufi (M.A., Universidade de São Paulo; Economics) February 12, 2010

Logan McLeod (Ph.D., McMaster University; Economics) November 13, 2009

Yifei Wang (M.A., McMaster University; Geography and Earth Sciences) September 18, 2009

Ivy Dam (M.A., McMaster University; Geography and Earth Sciences) September 18, 2009

Karen Wiley (M.A., McMaster University; Geography and Earth Sciences) September 10, 2009

Theodora Pouliou (Ph.D., McMaster University; Geography and Earth Sciences) September 8, 2009

Terry Li (Ph.D., The University of Queensland; School of Geography, Planning and Environmental Management) August, 2009

Gustavo Renno Rocha (M.Sc., Qualification Examination. Universidade de São Paulo; Escola de Engenharia de São Carlos) August 7, 2009

Dan Harrington (Ph.D., Comprehensive Examination. McMaster University; Geography and Earth Sciences) January 20, 2009

Kelsey MacCormack (Ph.D., Comprehensive Examination. McMaster University; Geography and Earth Sciences) September 22, 2008

Hejun Kang (Ph.D., McMaster University; Geography and Earth Sciences) August18, 2008

Kenneth Harold Doust (Ph.D., University of New South Wales, Australia; School of Civil and Environmental Engineering) May, 2008

Sylvia He (M.A., McMaster University; Geography and Earth Sciences) August 8, 2006

Jennifer L. Campos (Ph.D., McMaster University; Psychology and Neuroscience) September 11, 2007

Jessica Becker (M.A., McMaster University; Geography and Earth Sciences) September 17, 2007

Charles Cheung (Ph.D., University of New South Wales, Australia; School of Civil and Environmental Engineering) June, 2005

# Research and Other Funding

```{r research-funding-details}
read_csv(paste0(here(),"/assets/research-funding.csv")) |>
  arrange(desc(Year)) |>
  detailed_entries(what = Title, 
                   when = Year, 
                   where = Amount,
                   with = glue::glue("{Funder}, {Where}"),
                   why = glue::glue("PI: {PI}; team size: {Participants} researchers"),
                   .protect = FALSE)
```

# Research Impact

Fig. \ref{fig:citations} is a summary of research impact according to Google Scholar.

```{r citations-plot, fig.cap="\\label{fig:citations}Citations per year according to Google Scholar"}
id <- "bLY377kAAAAJ" # Replace with your own google scholar id
citations_scholar <- scholar::get_citation_history(id)

citations_scholar |>
  ggplot() + 
  geom_col(aes(x = year, 
               y = cites),
           color = "black",
           fill = "white") + 
  annotate(geom = "text", 
           x = 2004, 
           y = 950, 
           hjust = 0,
           label = paste0("Total cites = ", 
                          prettyNum(get_profile(id)$total_cites, big.mark = ","))) +
  annotate(geom = "text", 
           x = 2004, 
           y = 900, 
           hjust = 0,
           label = paste0("h-index = ", 
                          as.character(get_profile(id)$h_index))) +
  annotate(geom = "text", 
           x = 2004, 
           y = 850, 
           hjust = 0,
           label = paste0("i10-index = ", 
                          as.character(get_profile(id)$i10_index))) +
  ggthemes::theme_tufte()
```

<!--
\newpage
-->

# Lifetime Publications

## Books

```{r books}
bibliography_entries(paste0(here(),"/assets/books.bib")) |>
  arrange(desc(issued), desc(author$family))
```

## Edited Books

```{r edited-books}
bibliography_entries(paste0(here(),"/assets/edited-books.bib")) |>
#bibliography_entries(paste0(here(),"/assets/savedrecs_2.bib")) |>
  arrange(desc(issued), desc(author$family))
```

## Book Chapters

```{r book-chapters}
bibliography_entries(paste0(here(),"/assets/book-chapters.bib")) |>
#bibliography_entries(paste0(here(),"/assets/savedrecs_2.bib")) |>
  arrange(desc(issued), desc(author$family))
```

<!--
\newpage
-->

## Peer-Reviewed Journal Articles (Published)

```{r journal-articles-published}
bibliography_entries(paste0(here(),"/assets/refereed-publications.bib")) |>
  arrange(desc(issued), desc(author$family))
```

\newpage

## Peer-Reviewed Journal Articles (Accepted for Publication in Final Form)

```{r journal-articles-accepted-for-publication}
rpa <- bibliography_entries(paste0(here(),"/assets/refereed-publications-accepted.bib"))

# Check that the table is not empty
if(nrow(rpa) > 0){
  rpa |>
    arrange(desc(issued), desc(author$family))
}
```

<!--
\newpage
-->

## Peer-Reviewed Journal Articles (Submitted for Publication)

```{r journal-articles-submitted-for-publication}
rsp <- bibliography_entries(paste0(here(),"/assets/refereed-publications-submitted.bib")) 

# Check that the table is not empty
if(nrow(rpa) > 0){
  rsp |>
    arrange(desc(issued), desc(author$family))
}
```

<!--
\newpage
-->

## Peer-reviewed Conference Presentations

```{r peer-reviewed-conference-presentations}
bibliography_entries(paste0(here(),"/assets/conference-presentations-peer-reviewed.bib")) |>
  arrange(desc(issued), desc(author$family))
```

## Non-peer-reviewed Conference Presentations

```{r not-peer-reviewed-conference-presentations}
bibliography_entries(paste0(here(),"/assets/conference-presentations-not-peer-reviewed.bib")) |>
  arrange(desc(issued), desc(author$family))
```

# Unsolicited Advice

```{r unsolicited-advice-details}
read_csv(paste0(here(),"/assets/talks.csv")) |>
  filter(What == "Unsolicited Advice") |>
  detailed_entries(what = Organization, 
                   when = Year, 
                   with = Title,
                   where = Where,
                   why = paste0(What, ", ", Role),
                   .protect = FALSE)
```

# Invited Talks, Seminars, Workshops, Courses, and Panels

```{r talks-courses-details}
read_csv(paste0(here(),"/assets/talks.csv")) |>
  filter(What != "Unsolicited Advice") |>
  #slice_head(n = 39) |>
  detailed_entries(what = Organization, 
                   when = Year, 
                   with = Title,
                   where = Where,
                   why = paste0(What, ", ", Role),
                   .protect = FALSE)
```

# Departmental, Faculty, University Service

```{r internal-service-details}
read_csv(paste0(here(),"/assets/internal-service.csv")) |>
  detailed_entries(what = Position, 
                   when = Year, 
                   with = Organization,
                   where = Where)
```





