---
name: Antonio
surname: Páez
position: "Professor"
address: "School of Earth, Environment and Society, McMaster University, 1280 Main St West, Hamilton, Ontario, Canada L8S 1S4"
phone: +1 905 525 9140
www: experts.mcmaster.ca/display/paezha
email: "paezha@mcmaster.ca"
orcid: 0000-0001-6912-9919
github: paezha
publons: 2897251
#researchgate: 7004827878
googlescholar: paezha
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    page_total: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE)
library(here)
library(readr)
library(tibble)
library(vitae)
```

# About me

 * I trained in civil engineering before being adopted into geography.
 * My areas of interest are spatial analysis, spatial statistics, transportation, travel behavior, cities.
 * At this rate my only hope of being recognized is as most promising oldest researcher in my discipline.

# Education

```{r education-details}
read_csv(paste0(here(),"/assets/education.csv")) %>% 
  detailed_entries(what = Degree, 
                   when = Year, 
                   with = Institution,
                   where = Where, 
                   why = Thesis,
                   .protect = FALSE)
```

# Academic Employment

```{r employment-details}
read_csv(paste0(here(),"/assets/employment.csv")) %>% 
  detailed_entries(what = Position, 
                   when = Year, 
                   with = Organization,
                   where = Where,
                   .protect = FALSE)
```

# Employment in Industry

```{r}

```


# Peer-Reviewed Journal Articles

```{r}
bibliography_entries(paste0(here(),"/assets/refereed-publications.bib")) %>%
  arrange(desc(issued), desc(author$family))
```


