---
name: Antonio
surname: Páez
position: "Professor"
address: |
         | School of Earth, Environment and Society
         | McMaster University
         | 1280 Main St West, Hamilton, Ontario, Canada L8S 1S4
profilepic: apaez.jpg
phone: +1 905 525 9140
www: experts.mcmaster.ca/display/paezha
email: "paezha@mcmaster.ca"
orcid: 0000-0001-6912-9919
github: paezha
publons: 2897251
#researchgate: 7004827878
googlescholar: paezha
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "This is me."
output: vitae::twentyseconds
---

```{r knitr-setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE,
                      fig.show = "asis", 
                      out.width = "0.6\\linewidth", 
                      fig.align = "center")
```

```{r current-year}
# Retrieve current year
current_year <- as.numeric(as.character(Sys.time(), '%Y')) # Update year
```

```{r load-packages}
library(here)
library(readr)
library(scholar)
library(tibble)
library(tidyverse)
library(vitae)
```

# About me

 * I trained in civil engineering before being adopted into geography.
 * My areas of interest include spatial analysis, spatial statistics, transportation, travel behavior, cities.
 * Also, too, mathematics, computer languages, science fiction, poetry, and memes.
 * I have been known to look professorial on occasion.
 * At this rate my only hope of being recognized is as the most promising oldest researcher in my discipline.

# Education

```{r education-details}
read_csv(paste0(here(),"/assets/education.csv")) %>% 
  detailed_entries(what = Degree, 
                   when = Year, 
                   with = Institution,
                   where = Where, 
                   why = Thesis,
                   .protect = FALSE)
```

# Current Status at McMaster

Full Professor in the School of Earth, Environment and Society since 2014. Tenured since 2007.

# Employment History

## Academic

```{r employment-details}
read_csv(paste0(here(),"/assets/employment.csv")) %>% 
  detailed_entries(what = Position, 
                   when = Year, 
                   with = Organization,
                   where = Where,
                   .protect = FALSE)
```

## Industry

Surveyor and construction site supervisor (August 1993 – March 1995) Topographical
survey projects in Nuevo León, Mexico, sponsored by various Municipal Public Works Departments (Monterrey, Guadalupe, Santa Catarina), and by Mercedes-Benz. These projects involved in-field data collection and computer aided design. Construction site supervision.

\newpage

# Scholarly and Professional Activities

## Editor-in-Chief:

Journal of Geographical Systems (January, 2008-present)

## Associate Editor:

Papers in Regional Science (November, 2016-August, 2019)

## Editorial Board Membership

```{r editorial-board-details}
read_csv(paste0(here(),"/assets/editorial-board.csv")) %>%
  detailed_entries(what = Journal, 
                   when = Year,
                   .protect = FALSE)
```

## Journal Referee

```{r journal-referee}
referee <- read_csv(paste0(here(),"/assets/paper-reviews.csv")) %>% 
  pivot_longer(-Journal, 
               names_to = "Year", 
               values_to = "Reviews")
```

### Number of Total Lifetime Reviews

`r sum(referee$Reviews)`

### Number of Reviews in `r current_year`

`r referee %>% filter(Year == current_year) %>% pull(Reviews) %>% sum()`

### Reviews-to-Publications per Year

Fig. \ref{fig:reviews-pubs} is a summary of journal reviews-to-publications per year showing contributions to peer-review relative to demands on peer-review.

```{r reviews-per-year, include=FALSE, fig.cap="\\label{fig:reviews-annual-summary}Number of journal reviews per year"}
referee %>%
  group_by(Year) %>%
  summarize(Reviews = sum(Reviews),
            .groups = "drop") %>%
  ggplot() +
  geom_col(aes(x = Year, y = Reviews)) +
  ggthemes::theme_tufte() +
  theme(axis.text = element_text(angle = 45))
```

```{r review-to-publication, fig.cap="\\label{fig:reviews-pubs}Reviews-to-publications by year"}
# Check publication vs. review activity
df_pubs <- bibliography_entries(paste0(here(),"/assets/refereed-publications.bib"))
df_pubs <- data.frame(Year = df_pubs$issued %>% 
                        unlist()) %>%
  group_by(Year) %>%
  summarize(items = n(),
            .groups = "drop") %>%
  mutate(type = "Publication")

df_referee <- referee %>%
  group_by(Year) %>%
  summarize(items = sum(Reviews),
            .groups = "drop") %>%
  mutate(type = "Paper Review")

rbind(df_pubs,
      df_referee) %>%
  ggplot() +
  geom_col(aes(x = Year,
               y = items,
               fill = type),
           color = "black",
           position = position_dodge(preserve = "single")) +
  scale_fill_manual(values = c("Publication" = "white", "Paper Review" = "black")) +
  ggthemes::theme_tufte() +
  theme(axis.text.x = element_text(angle = 45),
        legend.title = element_blank())
```

### Reviews per journal

```{r journal-referee-details}
referee %>%
  group_by(Journal) %>% 
  summarize(Reviews = sum(Reviews), 
            .groups = "drop") %>%
  detailed_entries(what = Journal, 
                   when = Reviews,
                   .protect = FALSE)
```

# Areas of Interest

Spatial data analysis and statistics; transportation modeling; travel behavior; health geography; Geographic Information Systems.

# Honours

## Visiting Professorships

```{r professorship-details}
read_csv(paste0(here(),"/assets/honors.csv")) %>%
  dplyr::filter(Type == "Professorship") %>% 
  detailed_entries(what = Honor, 
                   when = Year, 
                   with = Organization,
                   where = Where,
                   .protect = FALSE)
```

## Scholarships

```{r scholarships-details}
read_csv(paste0(here(),"/assets/honors.csv")) %>%
  dplyr::filter(Type == "Scholarship") %>% 
  detailed_entries(what = Honor, 
                   when = Year, 
                   with = Organization,
                   where = Where,
                   .protect = FALSE)
```

## Scientific Awards

```{r scientific-awards-details}
read_csv(paste0(here(),"/assets/honors.csv")) %>%
  dplyr::filter(Type == "Scientific Awards") %>% 
  detailed_entries(what = Honor, 
                   when = Year, 
                   with = Organization,
                   where = Where,
                   why = With,
                   .protect = FALSE)
```

## Trainee Honours

```{r trainee-honors-details}
read_csv(paste0(here(),"/assets/honors.csv")) %>%
  dplyr::filter(Type == "Trainee") %>% 
  detailed_entries(what = Organization, 
                   when = Year, 
                   with = With,
                   where = Honor,
                   .protect = FALSE)
```

## Other

```{r other-honors-details}
read_csv(paste0(here(),"/assets/honors.csv")) %>%
  dplyr::filter(Type == "Other") %>% 
  mutate(Year = current_year) %>%
  detailed_entries(what = Organization, 
                   when = Year, 
                   with = Honor,
                   why = With,
                   .protect = FALSE) %>%
  mutate(Year = current_year)
```

# Supervisorships

## Undergraduate

## Diploma and Certificate

## Master

## Ph.D.

# Supervisory Committees

# Examination Committees

# Research and Other Funding

```{r research-funding-details}
read_csv(paste0(here(),"/assets/research-funding.csv")) %>%
  detailed_entries(what = Title, 
                   when = Year, 
                   where = Amount,
                   with = glue::glue("{Funder}, {Where}"),
                   why = glue::glue("PI: {PI}; team size: {Participants} researchers"),
                   .protect = FALSE)
```

# Research Impact

Fig. \ref{fig:citations} is a summary of research impact according to Google Scholar.

```{r citations-plot, fig.cap="\\label{fig:citations}Citations per year according to Google Scholar"}
id <- "bLY377kAAAAJ" # Replace with your own google scholar id
citations_scholar <- scholar::get_citation_history(id)

citations_scholar %>%
  ggplot() + 
  geom_col(aes(x = year, 
               y = cites),
           color = "black",
           fill = "white") + 
  annotate(geom = "text", 
           x = 2004, 
           y = 950, 
           hjust = 0,
           label = paste0("Total cites = ", 
                          prettyNum(get_profile(id)$total_cites, big.mark = ","))) +
  annotate(geom = "text", 
           x = 2004, 
           y = 900, 
           hjust = 0,
           label = paste0("h-index = ", 
                          as.character(get_profile(id)$h_index))) +
  annotate(geom = "text", 
           x = 2004, 
           y = 850, 
           hjust = 0,
           label = paste0("i10-index = ", 
                          as.character(get_profile(id)$i10_index))) +
  ggthemes::theme_tufte()
```

# Lifetime Publications

## Peer-Reviewed 

### Edited Books

```{r edited-books}
bibliography_entries(paste0(here(),"/assets/edited-books.bib")) %>%
#bibliography_entries(paste0(here(),"/assets/savedrecs_2.bib")) %>%
  arrange(desc(issued), desc(author$family))
```

### Book Chapters

### Journal Articles (Published)

```{r}
bibliography_entries(paste0(here(),"/assets/refereed-publications.bib")) %>%
#bibliography_entries(paste0(here(),"/assets/savedrecs_2.bib")) %>%
  arrange(desc(issued), desc(author$family))
```

### Journal Articles (Accepted for Publication in Final Form)

```{r}
bibliography_entries(paste0(here(),"/assets/refereed-publications-accepted.bib")) %>%
#bibliography_entries(paste0(here(),"/assets/savedrecs_2.bib")) %>%
  arrange(desc(issued), desc(author$family))
```

### Journal Articles (Submitted for Publication)

```{r}
bibliography_entries(paste0(here(),"/assets/refereed-publications-submitted.bib")) %>%
#bibliography_entries(paste0(here(),"/assets/savedrecs_2.bib")) %>%
  arrange(desc(issued), desc(author$family))
```

# Unsolicited Advice

```{r unsolicited-advice-details}
read_csv(paste0(here(),"/assets/talks.csv")) %>%
  filter(What == "Unsolicited Advice") %>%
  detailed_entries(what = Organization, 
                   when = Year, 
                   with = Title,
                   where = Where,
                   why = paste0(What, ", ", Role),
                   .protect = FALSE)
```

# Invited Talks, Seminars, Workshops, Courses, and Panels

```{r talks-courses-details}
read_csv(paste0(here(),"/assets/talks.csv")) %>%
  filter(What != "Unsolicited Advice") %>%
  detailed_entries(what = Organization, 
                   when = Year, 
                   with = Title,
                   where = Where,
                   why = paste0(What, ", ", Role),
                   .protect = FALSE)
```

# Departmental, Faculty, University Service

```{r internal-service-details}
read_csv(paste0(here(),"/assets/internal-service.csv")) %>%
  detailed_entries(what = Position, 
                   when = Year, 
                   with = Organization,
                   where = Where)
```
