---
name: Antonio
surname: Páez
position: "Professor"
address: |
         | School of Earth, Environment and Society
         | McMaster University
         | 1280 Main St West, Hamilton, Ontario, Canada L8S 1S4
         | phone: +1 905 525 9140
www: experts.mcmaster.ca/display/paezha
email: "paezha@mcmaster.ca"
orcid: 0000-0001-6912-9919
github: paezha
publons: 2897251
#researchgate: 7004827878
googlescholar: paezha
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
    page_total: true
    extra_dependencies: ["flafter"]
header-includes:
  - \usepackage{soul}
  - \usepackage{longtable}
  - \usepackage{float}
---


```{r knitr-setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE,
                      fig.show='asis', 
                      out.width="0.6\\linewidth", 
                      fig.align='center')

#pandoc::pandoc_activate()
```

```{r load-packages}
library(bibliometrix) # Comprehensive Science Mapping Analysis
library(dplyr) # A Grammar of Data Manipulation
library(ggraph) # An Implementation of Grammar of Graphics for Graphs and Networks
library(ggplot2) # Create Elegant Data Visualisations Using the Grammar of Graphics
library(glue) # Interpreted String Literals # Interpreted String Literals
library(gt) # Easily Create Presentation-Ready Display Tables
library(here) # A Simpler Way to Find Your Files # A Simpler Way to Find Your Files
library(kableExtra) # Construct Complex Table with 'kable' and Pipe Syntax 
library(lubridate) # Make Dealing with Dates a Little Easier
library(maps) # Draw Geographical Maps
library(readr) # Read Rectangular Text Data
library(rnaturalearth) # World Map Data from Natural Earth
library(rnaturalearthdata) # World Vector Map Data from Natural Earth Used in 'rnaturalearth'
library(scholar) # Analyse Citation Data from Google Scholar
library(sf) # Simple Features for R
library(stringr) # Simple, Consistent Wrappers for Common String Operations
library(tibble) # Simple Data Frames
library(tidygraph) # A Tidy API for Graph Manipulation
library(tidyr) # Tidy Messy Data
library(treemapify) # Draw Treemaps in 'ggplot2'
library(vitae) # Curriculum Vitae for R Markdown
```

```{r current-year}
# Retrieve current year
current_year <- lubridate::year(Sys.time()) # Update year
```

```{r google-scholar-id}
id <- "bLY377kAAAAJ" # Replace with your own google scholar id
```

# About this CV

This CV was created programmatically using the `R` statistical language, and it can be accessed here:  
https://github.com/paezha/Official-CV/blob/master/teaching-and-learning-cv/teaching-and-learning-cv.pdf

# About Me

* I trained in civil engineering before being adopted into geography.
* My areas of interest include transportation, equity, justice, spatial analysis, spatial statistics, travel behavior, and cities.
* Also, too, mathematics, computer languages, science fiction, poetry, and history.
* A 2024 global bibliometric analysis by [Research.com](https://research.com/scientists-rankings/social-sciences-and-humanities/ca) of the most influential scholars in the social sciences and humanities (about 16,000 researchers) places me in the **top 3%** of scholars in the world. 
<!-- Ranked 1904 of 16,000 (12%), and the 16,000 are already in the top 2% of scholars according to the Stanford Science Wide Indicators--> 
* In 2024 I was recognized with the **Edward L. Ullman Award** of the Association of American Geographers for lifelong commitment and contributions to the field of transportation geography.
* In 2010 a research team I led was recognized with the **Meredith F. Burrill Award** of the Association of American Geographers for exceptional work at the intersection of policy and basic research in geography.

# Education

```{r education-details}
read_csv(paste0(here(),"/assets/education.csv")) |> 
  detailed_entries(what = Degree, 
                   when = Year, 
                   with = Institution,
                   where = Where, 
                   why = Thesis,
                   .protect = FALSE)
```

# Current Status at McMaster

Full Professor in the School of Earth, Environment and Society since 2014. Tenured since 2007.

# Employment History

## Academic

```{r employment-details}
read_csv(paste0(here(),"/assets/employment.csv")) |> 
  slice_head(n = 4) |>
  detailed_entries(what = Position, 
                   when = Year, 
                   with = Organization,
                   where = Where,
                   .protect = FALSE)
```

<!--

## Industry
Surveyor and construction site supervisor (August 1993 - March 1995) Topographical
survey projects in Nuevo León, Mexico, sponsored by various Municipal Public Works Departments (Monterrey, Guadalupe, Santa Catarina), and by Mercedes-Benz.

Consultant (2015 - present) Environics Analytics, Toronto, Canada. 

# Honours

## Scientific Awards

```{r scientific-awards-details}
read_csv(paste0(here(),"/assets/honors.csv")) |>
  dplyr::filter(Type == "Scientific Awards") |> 
  arrange(desc(Year)) |>
  detailed_entries(what = Organization, 
                   when = Year, 
                   with = Honor,
                   where = Where,
                   why = With,
                   .protect = FALSE)
```

## Visiting Professorships

```{r professorship-details}
read_csv(paste0(here(),"/assets/honors.csv")) |>
  dplyr::filter(Type == "Professorship") |> 
  arrange(desc(Year)) |>
  detailed_entries(what = Honor, 
                   when = Year, 
                   with = Organization,
                   where = Where,
                   .protect = FALSE)
```

## Scholarships

```{r scholarships-details}
read_csv(paste0(here(),"/assets/honors.csv")) |>
  dplyr::filter(Type == "Scholarship") |>  
  arrange(desc(Year)) |>
  detailed_entries(what = Honor, 
                   when = Year, 
                   with = Organization,
                   where = Where,
                   .protect = FALSE)
```

## Trainee Honours

```{r trainee-honors-details}
read_csv(paste0(here(),"/assets/honors.csv")) |>
  dplyr::filter(Type == "Trainee") |> 
  detailed_entries(what = Organization, 
                   when = Year, 
                   with = With,
                   where = Honor,
                   .protect = FALSE)
```

# Editorial

## Editorships

```{r editor-details}
read_csv(paste0(here(),"/assets/editorial-board.csv")) |>
  filter(What == "Editor-in-Chief") |>
  detailed_entries(what = Journal, 
                   where = Year,
                   with = What,
                   .protect = FALSE)
```

```{r associate-editor-details}
read_csv(paste0(here(),"/assets/editorial-board.csv")) |>
  filter(What == "Associate Editor") |>
  detailed_entries(what = Journal, 
                   where = Year,
                   with = What,
                   .protect = FALSE)
```

## Guest Editorships

```{r guest-editor-details}
read_csv(paste0(here(),"/assets/editorial-board.csv")) |>
  filter(What == "Guest Editor") |>
  detailed_entries(what = Editors, 
                   when = Year,
                   with = What,
                   where = glue::glue("{Journal} {Volume}"),
                   why = Title,
                   .protect = FALSE)
```

## Editorial Boards

```{r editorial-board-details}
read_csv(paste0(here(),"/assets/editorial-board.csv")) |>
  filter(What == "Editorial Board Member") |>
  detailed_entries(what = Journal, 
                   where = Year,
                   with = What,
                   .protect = FALSE)
```

# Scholarly and Professional Activities

## Journal Referee

```{r journal-referee}
referee <- read_csv(paste0(here(),"/assets/paper-reviews.csv")) |> 
  pivot_longer(-Journal, 
               names_to = "Year", 
               values_to = "Reviews")
```

### Number of Total Lifetime Reviews

`r sum(referee$Reviews)`

### Number of Reviews in `r current_year`

`r referee |> filter(Year == current_year) |> pull(Reviews) |> sum()`

### Reviews-to-Publications per Year

Fig. \ref{fig:reviews-pubs} is a summary of journal reviews and publications per year. This is an indicator of my contributions to peer-reviewing relative to the demands my submissions put on peer-reviewers.

```{r reviews-per-year, include=FALSE, fig.cap="\\label{fig:reviews-annual-summary}Number of journal reviews per year"}
referee |>
  group_by(Year) |>
  summarize(Reviews = sum(Reviews),
            .groups = "drop") |>
  ggplot() +
  geom_col(aes(x = Year, y = Reviews)) +
  ggthemes::theme_tufte() +
  theme(axis.text = element_text(angle = 45))
```

```{r review-to-publication, fig.cap="\\label{fig:reviews-pubs}Reviews-to-publications by year"}
# Check publication vs. review activity
df_pubs <- bibliography_entries(paste0(here(),"/assets/refereed-publications.bib"))
df_pubs <- data.frame(Year = df_pubs$issued |> 
                        unlist()) |>
  group_by(Year) |>
  summarize(items = n(),
            .groups = "drop") |>
  mutate(type = "Publication")

df_referee <- referee |>
  group_by(Year) |>
  summarize(items = sum(Reviews),
            .groups = "drop") |>
  mutate(type = "Paper Review")

rbind(df_pubs,
      df_referee) |>
  ggplot() +
  geom_col(aes(x = Year,
               y = items,
               fill = type),
           color = "black",
           position = position_dodge(preserve = "single")) +
  scale_fill_manual(values = c("Publication" = "white", "Paper Review" = "black")) +
  ggthemes::theme_tufte() +
  theme(axis.text.x = element_text(angle = 45),
        legend.title = element_blank())
```

### Reviews per journal

```{r journal-referee-details}
referee |>
  group_by(Journal) |> 
  summarize(Reviews = sum(Reviews), 
            .groups = "drop") |>
  detailed_entries(what = Journal, 
                   when = Reviews,
                   .protect = FALSE)
```

# Grant Reviews

```{r}
read_csv(paste0(here(),"/assets/grant-reviews.csv")) |> 
  arrange(desc(Year)) |>
  detailed_entries(what = Role, 
                   when = glue::glue("Number of reviews: {Number}"), 
                   with = glue::glue("{Funder} ({Where})"),
                   where = Year,
                   .protect = FALSE)
```

-->

\newpage

# Areas of Interest

Transportation; accessibility; equity; justice; spatial data analysis and statistics; transportation modeling; travel behavior; health geography; Geographic Information Systems.


# Teaching at a Glance

```{r read-courses-asset}
courses <- read_csv(paste0(here(),"/assets/courses-taught.csv")) 
```

## Total number of courses taught

`r paste0("Undergraduate: ", courses |> filter(Level == "Undergraduate") |> nrow())`

`r paste0("Graduate: ", courses |> filter(Level == "Graduate") |> nrow())`

## Total number of students

`r paste0("Undergraduate: ", courses |> filter(Level == "Undergraduate") |> pull(Enrolment) |> sum() |> prettyNum(big.mark = ","))`

`r paste0("Graduate: ", courses |> filter(Level == "Graduate") |> pull(Enrolment) |> sum() |> prettyNum(big.mark = ","))`

# Teaching (Details)

## Undergraduate Teaching

```{r courses-brief-undergraduate}
courses <- read_csv(paste0(here(),"/assets/courses-taught.csv")) 

courses_summary <- courses |>
  group_by(Code) |> 
  summarize(Name = first(Name), 
            offerings = n(),
            total_students = sum(Enrolment), 
            level = first(Level)) |> 
  arrange(level)

courses_summary |>
  filter(level == "Undergraduate") |>
  detailed_entries(what = glue::glue("Total enrolment: {total_students} students"), 
                   with = Name,
                   where = glue::glue("Times offered: {offerings}"),
                   when = Code,
                   .protect = FALSE)
```

## Graduate Teaching

```{r courses-brief-graduate}
courses_summary |>
  filter(level == "Graduate") |>
  detailed_entries(what = glue::glue("Total enrolment: {total_students} students"), 
                   with = Name,
                   where = glue::glue("Times offered: {offerings}"),
                   when = Code,
                   .protect = FALSE)
```

## Diploma-Certificate Teaching

```{r courses-brief-diploma}
courses_summary |>
  filter(level == "Diploma-Certificate") |>
  detailed_entries(what = glue::glue("Total enrolment: {total_students} students"), 
                   with = Name,
                   where = glue::glue("Times offered: {offerings}"),
                   when = Code,
                   .protect = FALSE)
```

# Training of Highly Qualified Personnel

## Supervision at a Glance

```{r supervisorhip}
supervision <- read_csv(paste0(here(),"/assets/supervision.csv")) 
```

```{r supervision-at-a-glance}
supervision |>
  filter(is.na(With), Status != "Withdrew from Program") |>
  group_by(Level, Program) |>
  summarize(Supervision = n(),
            .groups = "drop") |>
  full_join(supervision |>
              filter(!is.na(With), Status != "Withdrew from Program") |>
              group_by(Level, Program) |>
              summarize(Cosupervision = n(),
                        .groups = "drop"),
            by = c("Level", "Program")) |>
  full_join(supervision |>
              filter(Status == "Withdrew from Program") |>
              group_by(Level, Program) |>
              summarize(Withdrew = n(),
                        .groups = "drop"),
            by = c("Level", "Program")) |>
  arrange(Level) |>
  mutate(Supervision = as.character(Supervision),
         Cosupervision = as.character(Cosupervision),
         Withdrew = as.character(Withdrew)) |>
  replace_na(list(Supervision = "-",
                  Cosupervision = "-",
                  Withdrew = "-")) |>
  gt() |>
  cols_label(Supervision = "Sole Supervisor",
             Cosupervision = "Co-supervisor",
             Withdrew = "Withdrawn from Program") |>
    as_latex()
```

## Undergraduate Supervision

```{r supervisorship-undergraduate}
supervision |>
  filter(Level == "Undergraduate") |>
  arrange(desc(Year), Program) |>
  detailed_entries(what = ifelse(!is.na(With), glue::glue("Co-supervised with {With}"), ""), 
                   with = glue::glue("{Name} ({Institution}, {Country})"),
                   where = case_when(Status == "Complete" ~ as.character(Year),
                                     Status == "In Progress" ~ "In Progress",
                                     Status == "Withdrew from Program" ~ "Withdrew from Program"),
                   when = Program,
                   .protect = FALSE)
```

## Master's Supervision

```{r supervisorship-masters}
supervision |>
  filter(Level == "Master") |>
  arrange(desc(Year)) |>
  detailed_entries(what = ifelse(!is.na(With), glue::glue("Co-supervised with {With}"), ""),
                   with = glue::glue("{Name} ({Institution}, {Country})"),
                   where = case_when(Status == "Complete" ~ as.character(Year),
                                     Status == "In Progress" ~ "In Progress",
                                     Status == "Withdrew from Program" ~ "Withdrew from Program"),
                   when = Program,
                   .protect = FALSE)
```

## Doctoral Supervision

```{r supervisorship-doctoral}
supervision |>
  filter(Level == "Doctoral") |>
  arrange(desc(Year)) |>
  detailed_entries(what = ifelse(!is.na(With), glue::glue("Co-supervised with {With}"), ""), 
                   with = glue::glue("{Name} ({Institution}, {Country})"),
                   where = case_when(Status == "Complete" ~ as.character(Year),
                                     Status == "In Progress" ~ "In Progress",
                                     Status == "Withdrew from Program" ~ "Withdrew from Program"),
                   when = Program,
                   .protect = FALSE)
```


# Supervisory Committees (All are doctoral unless otherwise noted)

Ricardo Lourenco Barros (McMaster University; 2022-) Understanding vegetation dynamics with satellite observations and Explainable Artificial Intelligence (XAI)

Samira Hamidetehrani (McMaster University; 2020-) User Preferences and Intentions Regarding Shared Automated Vehicles in Canadian Metropolitan Areas 

Christina Borowiec (McMaster University; 2019-) Active travel

Shaila Jamal (McMaster University; 2023) Generational differences in travel behavior 

Jeremy Gabriel (McMaster University; 2023) Strata analysis

Elnaz Abotalebi (McMaster University; 2019) Consumer stated preferences survey for electric cars

Wade Genders (McMaster University; 2018) Deep Reinforcement Learning Adaptive Traffic Signal Control 

Randy Bui (McMaster University; withdrew from program) Understanding Network Robustness and Critical Roadway Links in the Greater Toronto and Hamilton Area under Short-Term Disruption

Nazila Roofigari-Esfahan (McMaster University; 2016) A Framework for Spatio-Temporal Uncertainty-Aware Scheduling and Control of Linear Projects

Arash Olia (McMaster University; 2016) Modelling and Assessment of the Transportation Potential and Impacts of Connected and Automated Vehicles

Chris Higgins (McMaster University; 2015) A Value Planning Framework for Predicting and
Recapturing the Value of Rapid Transit Infrastructure

Matthew Adams (McMaster University; 2015) Advancing the use of mobile monitoring data for air pollution modelling

Scott Bennett (McMaster University; 2015) Safer walking routes to school: applied and methodological geographies of child pedestrian injury

Sarah Dickin (McMaster University; September 2014) Mapping vulnerability to water-related infectious disease: an ecosystem approach 

Ron Dalumpines (McMaster University; July 2014) Route choice analysis in time-geographic perspective

Kathleen Deutsch (University of California Santa Barbara; June 2013) Sense of place and travel behavior

Andrew Clarke (McMaster University; January 2013) Understanding determinants of active travel

Xudong Liu (McMaster University; withdrew from program in 2011) Integrating firmography in urban models

Jia Yang (McMaster University; withdrew from program in 2011) Modeling firm survival

Renilson Rodriguez da Silva (Universidade de Sao Paulo; completed: March 2011) Accessibility and development in the Amazon region (with Danilo Igliori)

Jamie E.L. Spinney (McMaster University; completed: September 2010) Geography, Land Values, and Municipal Taxation: A Spatial Paradigm for the Estimation and Reclamation of Rent

Kelsey MacCormack (McMaster University; completed: July 2010) Delineation of subsurface gravel units beneath the Dundas Valley, Ontario

Theodora Pouliou (McMaster University; completed: September 2009) Individual and Socio-Environmental Determinants of Obesity in Canada

Hejun Kang (McMaster University; completed: August 2008) Intra-households interactions and travel behavior

Dimitris Potoglou (McMaster University; completed: April 2006) Potential demand for alternative fuelled vehicles in the City of Hamilton CMA


# Examination Committees

Samira Hamidetehrani (Ph.D., McMaster University; School of Earth, Environment and Society ) September 15, 2023

Daniel Van Veghel (M.Sc., McMaster University; School of Earth, Environment and Society ) August 28, 2023

Bruno Dias dos Santos (M.Sc., INPE, Brazil) May 18, 2023

Daniela Arias Molinares (Ph.D., Facultad de Geografía e Historia, Universidad Complutense de Madrid) May 10, 2023

Shaila Jamal (Ph.D. McMaster University; School of Earth, Environment and Society) May 9, 2023

Lucy Joseph Chabariko (Ph.D., School of Transportation Sciences, University of Hasselt) December 21, 2020

Darcy Reynard (Ph.D., Department of Earth and Atmospheric Sciences, University of Alberta) December 18, 2020

Jose Carpio-Pinedo (Ph.D., ETS Arquitectura, Universidad Politecnica de Madrid) November 19, 2020

Sami Kurani (M.A., McMaster University; School of Earth, Environment and Society) September 28, 2020

Geun (Jayden) Choi (M.A., McMaster University; School of Earth, Environment and Society) August 25, 2020

Matthew Brown (M.A., McMaster University; School of Earth, Environment and Society) April 3, 2020

Javier Delso (Ph.D., ETSI Montes, Universidad Politecnica de Madrid) February 25, 2020

Shaila Jamal (Ph.D., Comprehensive Examination, School of Geography and Earth Sciences) February 11, 2020

Kyran Cupido (Ph.D., Arizona State University, School of Mathematics and Statistical Sciences) December 6, 2019

Zoha Anjum (MPH, McMaster University, Health Research Methods, Evidence, and Impact) September 2019

Georgios Sarlas (Ph.D., ETH Zurich, Civil, Environmental, and Geomatics Engineering) July 1, 2019

Matthew Quick (Ph.D., University of Waterloo; School of Planning) April 24, 2019

Wade Genders (Ph.D., McMaster University; Civil Engineering) November 22, 2018

Quinn Hachey (M.A., McMaster University; School of Geography and Earth Sciences) December 18, 2017

Wei Lu (M.A., McMaster University; School of Geography and Earth Sciences) September 28, 2017

Charles Burke (Ph.D., McMaster University; School of Geography and Earth Sciences) December 5, 2016

Nazila Roofigari-Esfahan (Ph.D., McMaster University; Civil Engineering) August 8, 2016

Juan Pablo Ospina Zapata (Ph.D., Comprehensive Examination. Universidad Nacional de Colombia – Medellin; Civil Engineering) June 10, 2016

Arash Olia (Ph.D., McMaster University; Civil Engineering) June 8, 2016

Geraldine Fuenmayor (Ph.D., University of Calgary; Civil Engineering) May 19, 2016

Sadia Yawar (M.A., McMaster University; School of Geography and Earth Sciences) April 29, 2016

An Neven (Ph.D., Hasselt University; School of Transportation Sciences) September 7, 2015

Chris Higgins (Ph.D., McMaster University; School of Geography and Earth Sciences) August 28, 2015

Matthew Adams (Ph.D., McMaster University; School of Geography and Earth Sciences) July 31, 2015

Scott Bennett (Ph.D., McMaster University; School of Geography and Earth Sciences) July 3, 2015

Wade Genders (M.A.Sc., McMaster University; Civil Engineering) November 17, 2014

Sarah Dickin (Ph.D., McMaster University; Geography) September 5, 2014

Simon Minelli (M.A.Sc., McMaster University; Civil Engineering) September 3, 2014

Ron Dalumpines (Ph.D., McMaster University; Geography) July 28, 2014

Markus Botte (Ph.D., University of Western Australia; Business) July 4, 2014

Kathleen Deutsch (Ph.D., University of California Santa Barbara; Geography) June 20, 2013

Chris Higgins (Ph.D., Comprehensive Examination. McMaster University; Geography and Earth Sciences) February 14, 2013

Andrew Clarke (Ph.D., McMaster University; Geography and Earth Sciences) September 24, 2012

Adrian Klisz (M.A., McMaster University; Geography and Earth Sciences) July 24, 2012

Sarah Dickin (Ph.D., Comprehensive Examination. McMaster University; Geography and Earth Sciences) October 24, 2011

Jia Yang (M.A., McMaster University; Geography and Earth Sciences) September 12, 2011

Xudong Liu (M.A., McMaster University; Geography and Earth Sciences) September 12, 2011 

Ron Dalumpines (Ph.D., Comprehensive Examination. McMaster University; Geography and Earth Sciences) December 3, 2010 

Jia Yang (Ph.D., Comprehensive Examination. McMaster University; Geography and Earth Sciences) December 2, 2010

Xudong Liu (Ph.D., Comprehensive Examination. McMaster University; Geography and Earth Sciences) December 2, 2010 

Jamie E.L. Spinney (Ph.D., McMaster University; Geography and Earth Sciences) September 24, 2010

Kelsey McCormack (Ph.D., McMaster University; Geography and Earth Sciences) July 27, 2010

PJ Saberton (M.A., McMaster University; Geography and Earth Sciences) July 26, 2010

Adam Drackley (M.A., McMaster University; Geography and Earth Sciences) July 26, 2010

Kathleen Deutsch (Ph.D., Proposal Defense. University of California Santa Barbara) April 14, 2010

Daniela Schettini (Ph.D., Universidade de São Paulo; Economics) April 9, 2010

Ana Maria Bonomi Barufi (M.A., Universidade de São Paulo; Economics) February 12, 2010

Logan McLeod (Ph.D., McMaster University; Economics) November 13, 2009

Yifei Wang (M.A., McMaster University; Geography and Earth Sciences) September 18, 2009

Ivy Dam (M.A., McMaster University; Geography and Earth Sciences) September 18, 2009

Karen Wiley (M.A., McMaster University; Geography and Earth Sciences) September 10, 2009

Theodora Pouliou (Ph.D., McMaster University; Geography and Earth Sciences) September 8, 2009

Terry Li (Ph.D., The University of Queensland; School of Geography, Planning and Environmental Management) August, 2009

Gustavo Renno Rocha (M.Sc., Qualification Examination. Universidade de São Paulo; Escola de Engenharia de São Carlos) August 7, 2009

Dan Harrington (Ph.D., Comprehensive Examination. McMaster University; Geography and Earth Sciences) January 20, 2009

Kelsey MacCormack (Ph.D., Comprehensive Examination. McMaster University; Geography and Earth Sciences) September 22, 2008

Hejun Kang (Ph.D., McMaster University; Geography and Earth Sciences) August18, 2008

Kenneth Harold Doust (Ph.D., University of New South Wales, Australia; School of Civil and Environmental Engineering) May, 2008

Sylvia He (M.A., McMaster University; Geography and Earth Sciences) August 8, 2006

Jennifer L. Campos (Ph.D., McMaster University; Psychology and Neuroscience) September 11, 2007

Jessica Becker (M.A., McMaster University; Geography and Earth Sciences) September 17, 2007

Charles Cheung (Ph.D., University of New South Wales, Australia; School of Civil and Environmental Engineering) June, 2005

# Funding for Teaching and Learning

```{r research-funding}
research_funding <- read_csv(paste0(here(),"/assets/research-funding.csv")) |>
  filter(Purpose == "Teaching") |>
  mutate(Amount_num = str_replace_all(Amount, ",", ""),
         Amount_num = str_extract_all(Amount_num, "\\d+") |>
           as.numeric(),
         Share = Amount_num * Share,
         Share_chr = prettyNum(Share, big.mark =",", digits = 4),
         Share_chr = paste0("$", Share_chr))
```

I have been the recipient of several grants to improve teaching practice, to the total of `r paste0("CAD ", prettyNum(sum(research_funding$Amount_num[research_funding$Purpose == "Teaching"]), big.mark = ",", digits = 4))`. The funding sources as well as the projects are as shown below. 

```{r research-funding-details}
read_csv(paste0(here(),"/assets/research-funding.csv")) |>
  filter(Purpose == "Teaching") |>
  arrange(desc(Year)) |>
  detailed_entries(what = Title, 
                   when = Year, 
                   where = Amount,
                   with = glue::glue("{Funder}, {Where}"),
                   why = glue::glue("PI: {PI}; team size: {Participants} researchers"),
                   .protect = FALSE)
```

# Open Educational Resources

## Books

```{r oer-books}
bibliography_entries(paste0(here(),"/assets/books.bib")) |>
  filter(note == "Open Educational Resource") |>
  arrange(desc(issued), desc(author$family))
```

## Packages

```{r oer-packages}
bibliography_entries(paste0(here(),"/assets/packages.bib")) |>
  arrange(desc(issued), desc(author$family))
```

# Research

Research related to teaching and learning.

## Peer reviewed

```{r pedagogical-research}
bibliography_entries(paste0(here(),"/assets/refereed-publications.bib")) |>
  filter(note == "Pedagogical Research") |>
  arrange(desc(issued), desc(author$family))
```

## Work in Progress

```{r work-in-progress}
bibliography_entries(paste0(here(),"/assets/work-in-progress.bib")) |>
  filter(note == "Pedagogical Research") |>
  arrange(desc(issued), desc(author$family))
```