---
title: "Antonio Páez"
author: Antonio Paez
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true
# uncomment this line to produce HTML and PDF in RStudio:
knit: pagedown::chrome_print
---

```{r knitr-setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE,
                      fig.show='asis', 
                      out.width="0.6\\linewidth", 
                      fig.align='center')
```

```{r load-packages}
library(glue)
library(here)
library(readr)
library(scholar)
library(tibble)
library(tidyverse)
library(vitae)
```

Aside
================================================================================

![Antonio Paez](https://avatars.githubusercontent.com/u/30074724)

Contact Info {#contact}
--------------------------------------------------------------------------------

- <i class="fa fa-envelope"></i> paezha@mcmaster.ca
- <i class="fa fa-github"></i> [github.com/paezha](https://github.com/paezha)
- School of Earth, Environment and Society, McMaster University
- 1280 Main Street West, Hamilton, Ontario, L8S 4K1 Canada
- The full version of this CV is available [here](https://github.com/paezha/Official-CV/blob/master/awesomecv/awesomecv.pdf).


About me {#about-me}
--------------------------------------------------------------------------------

- I trained in civil engineering before being adopted into geography.
- My areas of interest include spatial analysis, spatial statistics, transportation, travel behavior, cities.

Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Made in `R` with [**pagedown**](https://github.com/rstudio/pagedown).

Last updated on `r Sys.Date()`.

Main
================================================================================

Antonio Páez {#title}
--------------------------------------------------------------------------------

### Professor, School of Earth, Environment and Society
### McMaster University

Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r process-education-details}
df <- read_csv(paste0(here(),"/assets/education.csv")) %>%
  replace_na(list(Thesis = "")) %>%
  mutate(across(.cols = everything(),
                ~ replace_na(.x, "")),
         across(.cols = everything(), 
                ~ str_replace_all(.x, 
                                  "\\\\\'\\{a\\}",
                                  "á")),
         across(.cols = everything(), 
                ~ str_replace_all(.x, 
                                  "\\\\\'\\{e\\}",
                                  "é")),
         across(.cols = everything(), 
                ~ str_replace_all(.x, 
                                  "\\\\\'\\{i\\}",
                                  "í")),
         across(.cols = everything(), 
                ~ str_replace_all(.x, 
                                  "\\\\\'\\{o\\}",
                                  "ó")),
         across(.cols = everything(),
                ~ str_replace_all(.x, 
                                  "\\\\\'\\{u\\}",
                                  "ú")))
```

```{r education-details, results='asis'}
df %>% 
  glue_data(
   "### {Institution}",
   "\n\n",
   "{Degree}",
   "\n\n",
   "{Where}",
   "\n\n",
   "{Year}", 
   "\n\n",
   "{Thesis}",
   "\n\n\n"
 )
```

Academic Experience {data-icon=laptop}
--------------------------------------------------------------------------------

```{r process-employment-details}
df <- read_csv(paste0(here(),"/assets/employment.csv"))  %>%
  select(-Type) %>%
  #replace_na(list(Thesis = "")) %>%
  mutate(across(.cols = everything(),
                ~ replace_na(.x, "")),
         across(.cols = everything(), 
                ~ str_replace_all(.x, 
                                  "\\\\\'\\{a\\}",
                                  "á")),
         across(.cols = everything(), 
                ~ str_replace_all(.x, 
                                  "\\\\\'\\{e\\}",
                                  "é")),
         across(.cols = everything(), 
                ~ str_replace_all(.x, 
                                  "\\\\\'\\{i\\}",
                                  "í")),
         across(.cols = everything(), 
                ~ str_replace_all(.x, 
                                  "\\\\\'\\{o\\}",
                                  "ó")),
         across(.cols = everything(),
                ~ str_replace_all(.x, 
                                  "\\\\\'\\{u\\}",
                                  "ú")))
```

```{r employment-details, results='asis'}
df %>% 
  glue_data(
   "### {Position}",
   "\n\n",
   "{Organization}",
   "\n\n",
   "{Where}",
   "\n\n",
   "{Year}",
   "\n\n\n"
 )
```

<!--
Professional Experience {data-icon=suitcase}
--------------------------------------------------------------------------------

### Data Scientist, intern

SupStat Inc.

Beijing, China

2014

::: concise
- Taught R language to beginners. 
- Wrote Shiny app demos.
- Converted statistical tutorials from SPSS to R language.
:::

### Bioinformatician

My Health Gene Technology Co., Ltd.

Beijing, China

2015 - 2016

::: concise
- Analyzed whole-exome sequencing data. 
- Wrote analysis pipelines of ChIP-seq, single cell DNA-seq and single cell RNA-seq.
- Studied tumor metastasis and wrote research reports. 
- Also did case studies to identify the genetic defect causing rare disease.
:::


Teaching Experience {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

### Introduction to R Language for Beginners.

Instructor of R and Data Mining Training Courses at SupStat Inc.

Beijing, China
-->

Selected Publications {data-icon=file}
--------------------------------------------------------------------------------

```{r selected-publications, results='asis'}
id <- "bLY377kAAAAJ"
get_publications(id) %>% 
  arrange(desc(cites)) %>% 
  slice_head(n = 10) %>%
  glue_data(
   "### {author} ({year})",
   "\n\n",
   "{title}. {journal}, {number}",
   "\n\n",
   "Number of cites (Google Scholar): {cites}",
   "\n\n",
   " ",
   "\n\n\n"
 )

```

